### 2014-05-12 proposal/proposal.tex
Wrote out a proposal. It's not great

\documentclass{article}
\usepackage{float}
\usepackage[margin=1.5in]{geometry}
\usepackage{setspace}

\onehalfspacing

\begin{document}
\large
\thispagestyle{empty}

\section*{Project Title}

{\bf Using a maximum entropy classifier for Sentiment analysis of Twitter Data}

\quad

This project will be carried out by Douglas Anderson in the summer of 2014,
under the supervision of Professor Fei Song.

\section*{Subject Description and Expected Results}

Determining public sentiment is a difficult task that can help Governments,
Companies, and Organizations make more informed decisions. In the modern era of
social media we have an opportunity to gauge people's feeling about events
mechanically using Natural Language Processing techniques.

The dataset and inspiration for the project is the provided by Task B outlined
in task 2 of the 2013 International Workshop on Sentiment Analysis
(http://www.cs.york.ac.uk/semeval-2013/task2/). The goal is to create a
classifier (or set of classifiers) that will reliably determine the message
polarity of a Twitter Message (a `tweet'). The constrained nature of tweets
lead to abbreviations and their informality leads to incorrect spelling and
grammar. These issues can add difficulty to the classification process.

The maximum entropy modelling is a machine learning approach that has, in
previous work, performed well in loosely structure text. Over the course of the
semester Douglas will design, implement, test and report upon possible
improvements on existing classification methods.

\section*{Evaluation Method}

\begin{itemize}
    \item Literature survey: 15\%
    \item Discussion, analysis ad design: 30\%
    \item Implementation, testing and experimental results: 30\%
    \item Final oral presentation and written synthesis: 25\%
\end{itemize}

\end{document}

### 2014-07-23 src/InvertedList.py
Removed the inverted list I never started and removing the scanner binary from version control.

@@ -1,22 +1,0 @@
-#!/usr/bin/env python
-
-# File       : InvertedList.py
-# Author     : Douglas Anderson
-# Description: Records the words in an inverted list structure
-
-class InvertedList:
-    words = []
-    posting = []
-    docs = []
-
-    def __init__(self):
-        pass
-
-    def add(self, token):
-        print token.__unicode__()
-        if token.tokentype == "word":
-            words.add()
-        # Add the word to word list
-        # Add that to the posting
-        # Add the number of times the words occurs in the doc
-

### 2014-07-24 src/conductor.py
Adding a new dataset.

@@ -43,7 +43,7 @@ def parse_args():
 if __name__ == "__main__":
     args = parse_args()
     print "Opening dataset..."
-    tokens = tokenize.open_tweets_file("../data/b.tsv", 0, args.items)
+    tokens = tokenize.open_tweets_file("../data/b.2.tsv", 0, args.items)
 
     print "Selecting labels..."
     tokens = labelselect.__call__(tokens, args.labels) # Select only the labels

### 2014-07-24 src/tokenize.py

@@ -36,7 +36,7 @@ def create_tweetid(sid, uid):
 def open_tweets_file(filename, start, end):
     count = 0
     tokens = []
-    with open("../data/b.tsv") as f:
+    with open(filename) as f:
         r = csv.DictReader(f, delimiter="\t")
         for tweet in r:
             if count >= start and count < end:

### 2014-07-24 src/statsify.py
Done the fscore for the new labels

@@ -70,10 +70,6 @@ def calculate_confusion_matrix(cc):
                 for other_other_label in cc.keys():
                     if label != other_other_label:
                         label_stats[label]["fn"] += cc[other_other_label][other_label]
-        #print label, "tp:\t", label_stats[label]["tp"]
-        #print label, "tn:\t", label_stats[label]["tn"]
-        #print label, "fp:\t", label_stats[label]["fp"]
-        #print label, "fn:\t", label_stats[label]["fn"]
     return(label_stats)
 
 def multi_label_classifier_test(classifier, test_set):
@@ -123,7 +119,12 @@ def bi_label_classifier_test(classifier, test_set):
         cm_raw[result][intended_label] += 1
     print_bi_confusion_matrix(cm_raw)
 
+    precison = cm_raw["positive"]["positive"] / float(cm_raw["positive"]["positive"] + cm_raw["positive"]["negative"])
+    recall = cm_raw["positive"]["positive"] / float(cm_raw["positive"]["positive"] + cm_raw["negative"]["positive"])
+    fscore = 2 * ((precison * recall)/(precison + recall))
+
     print "Accuracy  :\t", nltk.classify.accuracy(classifier, test_set)
-    print "Precision :\t", cm_raw["positive"]["positive"] / float(cm_raw["positive"]["positive"] + cm_raw["positive"]["negative"])
-    print "Recall    :\t", cm_raw["positive"]["positive"] / float(cm_raw["positive"]["positive"] + cm_raw["negative"]["positive"])
+    print "Precision :\t", precison
+    print "Recall    :\t", recall
+    print "Fscore    :\t", fscore
 

### 2014-07-24 src/conductor.py
Created a classifer with a validation set. Also added operations to the makefile

@@ -16,7 +16,7 @@ import wordselection
 import dictizer
 import split_dataset
 from Token import Token
-from train import multi_label_classifier, multi_label_naive_bayes_classifier
+from train import multi_label_classifier, multi_label_classifier_with_validation, multi_label_naive_bayes_classifier
 
 def parse_args():
     classifier_types = ["max_ent", "bayes"]
@@ -28,6 +28,8 @@ def parse_args():
     parser.add_argument("--minlldelta", type=float,
             help="This parameter changes the cutoff of training for max ent ")
     parser.add_argument("--minll", type=float,
+            help="This parameter changes the cutoff for training for max ent ")
+    parser.add_argument("--validationAccuracy", type=float,
             help="This parameter changes the cutoff for training for max ent ")
     parser.add_argument("--classifier_type", default="max_ent",
             help="Select classifer should be:" + " ".join(classifier_types))
@@ -58,7 +60,10 @@ if __name__ == "__main__":
     feature_list = wordselection.__call__(feature_list)
 
     print "Splitting the dataset..."
-    train_set, test_set = split_dataset.__call__(feature_list, 0.2)
+    if not args.validationAccuracy:
+        train_set, _, test_set = split_dataset.__call__(feature_list, 0.2)
+    else:
+        train_set, validation_set, test_set = split_dataset.__call__(feature_list, 0.2, validation_size=0.15)
 
     # Write the features out to a file
     with open("filtered_docs.txt", "w") as w:
@@ -73,6 +78,8 @@ if __name__ == "__main__":
             classifier = multi_label_classifier(train_set, lldelta=args.minlldelta)
         elif args.minll:
             classifier = multi_label_classifier(train_set, ll=args.minll)
+        elif args.validationAccuracy:
+            classifier = multi_label_classifier_with_validation(train_set, validation_set, args.validationAccuracy)
         else:
             classifier = multi_label_classifier(train_set)
     else:

### 2014-07-24 src/split_dataset.py

@@ -16,7 +16,10 @@ def __call__(feature_list, test_size, validation_size=0.0):
         x = random.randint(0, len(feature_list)-1)
         test_set.append(feature_list[x])
         del feature_list[x]
-    #TODO validation set
+    while len(validation_set) < int(math.ceil((len(feature_list) * validation_size))):
+        x = random.randint(0, len(feature_list)-1)
+        validation_set.append(feature_list[x])
+        del feature_list[x]
     train_set = feature_list
-    return train_set, test_set
+    return train_set, validation_set, test_set
 

### 2014-07-24 src/train.py

@@ -1,9 +1,13 @@
 #!/usr/bin/env python
 
 import nltk
+import numpy
 import statsify
 
 from nltk.featstruct import FeatStruct
+from nltk.classify.maxent import CutoffChecker, BinaryMaxentFeatureEncoding, calculate_empirical_fcount
+from nltk.classify.maxent import calculate_nfmap, ConditionalExponentialClassifier, log_likelihood, accuracy
+from nltk.classify.maxent import calculate_deltas
 
 class classifier:
     def __init__(self, train_set):
@@ -39,6 +43,110 @@ class multi_label_classifier(classifier):
         else:
             print "Cutoff after 50 iterations"
             self.classifier = nltk.MaxentClassifier.train(train_set, max_iter=50)
+
+def train_maxent_classifier_with_iis_with_validation(train_toks, prev_weights=None, trace=3, encoding=None,
+                                     labels=None, **cutoffs):
+    """
+    Derived from train_maxent_classifier_with_iis
+    """
+    cutoffs.setdefault('max_iter', 100)
+    cutoffchecker = CutoffChecker(cutoffs)
+
+    # Construct an encoding from the training data.
+    if encoding is None:
+        encoding = BinaryMaxentFeatureEncoding.train(train_toks, labels=labels)
+
+    # Count how many times each feature occurs in the training data.
+    empirical_ffreq = (calculate_empirical_fcount(train_toks, encoding) /
+                       len(train_toks))
+
+    # Find the nf map, and related variables nfarray and nfident.
+    # nf is the sum of the features for a given labeled text.
+    # nfmap compresses this sparse set of values to a dense list.
+    # nfarray performs the reverse operation.  nfident is
+    # nfarray multiplied by an identity matrix.
+    nfmap = calculate_nfmap(train_toks, encoding)
+    nfarray = numpy.array(sorted(nfmap, key=nfmap.__getitem__), 'd')
+    nftranspose = numpy.reshape(nfarray, (len(nfarray), 1))
+
+    # Check for any features that are not attested in train_toks.
+    unattested = set(numpy.nonzero(empirical_ffreq==0)[0])
+
+    # Build the classifier.  Start with weight=0 for each attested
+    # feature, and weight=-infinity for each unattested feature.
+    if prev_weights == None:
+        weights = numpy.zeros(len(empirical_ffreq), 'd')
+        for fid in unattested: weights[fid] = numpy.NINF
+    else:
+        weights = prev_weights
+    classifier = ConditionalExponentialClassifier(encoding, weights)
+
[…]

### 2014-07-24 src/statsify.py
Added tiny and div by zero catches

@@ -119,9 +119,18 @@ def bi_label_classifier_test(classifier, test_set):
         cm_raw[result][intended_label] += 1
     print_bi_confusion_matrix(cm_raw)
 
-    precison = cm_raw["positive"]["positive"] / float(cm_raw["positive"]["positive"] + cm_raw["positive"]["negative"])
-    recall = cm_raw["positive"]["positive"] / float(cm_raw["positive"]["positive"] + cm_raw["negative"]["positive"])
-    fscore = 2 * ((precison * recall)/(precison + recall))
+    try:
+        precison = cm_raw["positive"]["positive"] / float(cm_raw["positive"]["positive"] + cm_raw["positive"]["negative"])
+    except:
+        precison = 0.0
+    try:
+        recall = cm_raw["positive"]["positive"] / float(cm_raw["positive"]["positive"] + cm_raw["negative"]["positive"])
+    except:
+        recall = 0.0
+    try:
+        fscore = 2 * ((precison * recall)/(precison + recall))
+    except:
+        fscore = 0.0
 
     print "Accuracy  :\t", nltk.classify.accuracy(classifier, test_set)
     print "Precision :\t", precison

### 2014-07-24 src/conductor.py
Added an option for a counted number of iterations

@@ -30,9 +30,11 @@ def parse_args():
     parser.add_argument("--minll", type=float,
             help="This parameter changes the cutoff for training for max ent ")
     parser.add_argument("--validationAccuracy", type=float,
+            help="This parameter changes the cutoff for training for max ent ") # TODO make this validationDelta
+    parser.add_argument("--numIterations", type=int,
             help="This parameter changes the cutoff for training for max ent ")
     parser.add_argument("--classifier_type", default="max_ent",
-            help="Select classifer should be:" + " ".join(classifier_types))
+            help="Select classifier should be:" + " ".join(classifier_types))
     parser.add_argument("--labels", default="pn",
             help="Which labels should be:" + " ".join(labels))
     args = parser.parse_args()
@@ -60,10 +62,10 @@ if __name__ == "__main__":
     feature_list = wordselection.__call__(feature_list)
 
     print "Splitting the dataset..."
-    if not args.validationAccuracy:
+    if args.validationAccuracy == None:
         train_set, _, test_set = split_dataset.__call__(feature_list, 0.2)
     else:
-        train_set, validation_set, test_set = split_dataset.__call__(feature_list, 0.2, validation_size=0.15)
+        train_set, validation_set, test_set = split_dataset.__call__(feature_list, 0.2, validation_size=0.2)
 
     # Write the features out to a file
     with open("filtered_docs.txt", "w") as w:
@@ -78,10 +80,13 @@ if __name__ == "__main__":
             classifier = multi_label_classifier(train_set, lldelta=args.minlldelta)
         elif args.minll:
             classifier = multi_label_classifier(train_set, ll=args.minll)
-        elif args.validationAccuracy:
+        elif args.validationAccuracy != None:
             classifier = multi_label_classifier_with_validation(train_set, validation_set, args.validationAccuracy)
+        elif args.numIterations:
+            classifier = multi_label_classifier(train_set, iterations=args.numIterations)
         else:
-            classifier = multi_label_classifier(train_set)
+            print "Error no cut off set"
+            sys.exit(0)
     else:
         classifier = multi_label_naive_bayes_classifier(train_set)
 

### 2014-07-24 src/train.py

@@ -33,7 +33,7 @@ class classifier:
 
 
 class multi_label_classifier(classifier):
-    def __init__(self, train_set, lldelta=None, ll=None):
+    def __init__(self, train_set, iterations=None, lldelta=None, ll=None):
         if lldelta:
             print "Cutoff after log likelyhood changes by less than", lldelta
             self.classifier = nltk.MaxentClassifier.train(train_set, min_lldelta=lldelta)
@@ -41,8 +41,10 @@ class multi_label_classifier(classifier):
             print "Cutoff after log likelyhood reaches", ll
             self.classifier = nltk.MaxentClassifier.train(train_set, min_ll=ll)
         else:
-            print "Cutoff after 50 iterations"
-            self.classifier = nltk.MaxentClassifier.train(train_set, max_iter=50)
+            if not iterations:
+                iterations = 25
+            print "Cutoff after {} iterations".format(iterations)
+            self.classifier = nltk.MaxentClassifier.train(train_set, max_iter=iterations)
 
 def train_maxent_classifier_with_iis_with_validation(train_toks, prev_weights=None, trace=3, encoding=None,
                                      labels=None, **cutoffs):
@@ -130,7 +132,7 @@ def train_maxent_classifier_with_iis_with_validation(train_toks, prev_weights=No
 class multi_label_classifier_with_validation(classifier):
     def __init__(self, train_set, validation_set, accuracy_delta_cutoff):
         print "Cutoff after validation set reaches {}% accuracy".format(accuracy_delta_cutoff)
-        self.classifier = nltk.MaxentClassifier.train(train_set, max_iter=5)
+        self.classifier = nltk.MaxentClassifier.train(train_set, trace=1, max_iter=5)
         iter_count = 0
         prev_accuracy = 0.0
         accuracy = nltk.classify.accuracy(self.classifier, validation_set)
@@ -139,7 +141,7 @@ class multi_label_classifier_with_validation(classifier):
         while (accuracy - prev_accuracy) > accuracy_delta_cutoff:
             iter_count += 1
             prev_weights = self.classifier.weights()
-            self.classifier = train_maxent_classifier_with_iis_with_validation(train_set, prev_weights=prev_weights, max_iter=5)
+            self.classifier = train_maxent_classifier_with_iis_with_validation(train_set, trace=1, prev_weights=prev_weights, max_iter=1)
             prev_accuracy = accuracy
[…]

### 2014-07-24 paper/paper.tex
Started to stub out the write up.

\documentclass[12pt]{article}
\usepackage{enumerate}
\usepackage{courier}
\usepackage{graphicx}
\usepackage[margin=1.0in]{geometry}
\usepackage{float}
\usepackage{setspace}

\onehalfspacing
%\doublespacing
\restylefloat{table}

\makeatletter
\renewcommand\@seccntformat[1]{}
\makeatother

\begin{document}

\thispagestyle{empty}
\begin{center}

\huge

Utilizing maximum entropy classifiers for sentiment analysis in twitter messages

\large
\vspace{2.0cm}
By

\vspace{1.0cm}
Douglas Anderson

0703557

dander01@uoguelph.ca

\vspace{1.5cm}
CIS*4900 - Undergraduate Research Project

August 1, 2014 %TODO fix this

\vspace{1.5cm}

Supervisor:

Professor Fei Song

\vspace{1.5cm}

Second Reader:

Professor Lee % TODO which professor Lee?

\end{center}

\newpage
\pagestyle{headings}
\setcounter{page}{1}

\section{Introduction}

\subsection{Topic Area}
\subsection{Specific Problem}
\subsection{Task Description}

\section{Background}

\section{Approach}

\section{Discussion}

\section{Conclusion}

\section{Future Work}

\section{Works Cited}

\end{document}

### 2014-07-25 src/conductor.py
Added different fscore to control validation training

@@ -16,11 +16,14 @@ import wordselection
 import dictizer
 import split_dataset
 from Token import Token
-from train import multi_label_classifier, multi_label_classifier_with_validation, multi_label_naive_bayes_classifier
+from train import maxent_classifier
+from train import maxent_classifier_with_validation
+from train import naive_bayes_classifier
 
 def parse_args():
     classifier_types = ["max_ent", "bayes"]
     labels = ["pn", "pnn"]
+    val_metrics = ["none", "accuracy", "fscore"]
     parser = argparse.ArgumentParser(description="Scan a tweet to determine it's tokens")
     parser.add_argument("--file", type=str,
             help="The file name containing the text to be scanned")
@@ -29,10 +32,10 @@ def parse_args():
             help="This parameter changes the cutoff of training for max ent ")
     parser.add_argument("--minll", type=float,
             help="This parameter changes the cutoff for training for max ent ")
-    parser.add_argument("--validationAccuracy", type=float,
-            help="This parameter changes the cutoff for training for max ent ") # TODO make this validationDelta
     parser.add_argument("--numIterations", type=int,
             help="This parameter changes the cutoff for training for max ent ")
+    parser.add_argument("--validationMetric", default="none",
+            help="This changes the metric for validation set evaluation")
     parser.add_argument("--classifier_type", default="max_ent",
             help="Select classifier should be:" + " ".join(classifier_types))
     parser.add_argument("--labels", default="pn",
@@ -42,6 +45,8 @@ def parse_args():
         raise Exception("Classifier type must be one of: " + " ".join(classifier_types))
     if args.labels not in labels:
         raise Exception("Labels must be one of: " + " ".join(labels))
+    if args.validationMetric not in val_metrics:
+        raise Exception("Validation metrics must be one of: " + " ".join(val_metrics))
     return args
 
 if __name__ == "__main__":
@@ -62,7 +67,7 @@ if __name__ == "__main__":
     feature_list = wordselection.__call__(feature_list)
 
     print "Splitting the dataset..."
-    if args.validationAccuracy == None:
+    if args.validationMetric == "none":
         train_set, _, test_set = split_dataset.__call__(feature_list, 0.2)
     else:
         train_set, validation_set, test_set = split_dataset.__call__(feature_list, 0.2, validation_size=0.2)
@@ -77,18 +82,19 @@ if __name__ == "__main__":
 
     if args.classifier_type == "max_ent":
         if args.minlldelta:
[…]

### 2014-07-25 src/maxent_classifier_with_validation.py

@@ -1,0 +1,90 @@
+import numpy
+
+from nltk.classify.maxent import CutoffChecker, BinaryMaxentFeatureEncoding
+from nltk.classify.maxent import calculate_nfmap, ConditionalExponentialClassifier
+from nltk.classify.maxent import calculate_deltas, log_likelihood, accuracy
+from nltk.classify.maxent import calculate_empirical_fcount
+
+def train_maxent_classifier_with_validation(train_toks, prev_weights=None,
+        trace=3, encoding=None, labels=None, **cutoffs):
+    """
+    Derived from train_maxent_classifier_with_iis
+    """
+    cutoffs.setdefault('max_iter', 100)
+    cutoffchecker = CutoffChecker(cutoffs)
+
+    # Construct an encoding from the training data.
+    if encoding is None:
+        encoding = BinaryMaxentFeatureEncoding.train(train_toks, labels=labels)
+
+    # Count how many times each feature occurs in the training data.
+    empirical_ffreq = (calculate_empirical_fcount(train_toks, encoding) /
+                       len(train_toks))
+
+    # Find the nf map, and related variables nfarray and nfident.
+    # nf is the sum of the features for a given labeled text.
+    # nfmap compresses this sparse set of values to a dense list.
+    # nfarray performs the reverse operation.  nfident is
+    # nfarray multiplied by an identity matrix.
+    nfmap = calculate_nfmap(train_toks, encoding)
+    nfarray = numpy.array(sorted(nfmap, key=nfmap.__getitem__), 'd')
+    nftranspose = numpy.reshape(nfarray, (len(nfarray), 1))
+
+    # Check for any features that are not attested in train_toks.
+    unattested = set(numpy.nonzero(empirical_ffreq==0)[0])
+
+    # Build the classifier.  Start with weight=0 for each attested
+    # feature, and weight=-infinity for each unattested feature.
+    if prev_weights == None:
+        weights = numpy.zeros(len(empirical_ffreq), 'd')
+        for fid in unattested: weights[fid] = numpy.NINF
+    else:
+        weights = prev_weights
+    classifier = ConditionalExponentialClassifier(encoding, weights)
+
+    if trace > 0: print('  ==> Training (%d iterations)' % cutoffs['max_iter'])
+    if trace > 2:
+        print()
+        print('      Iteration    Log Likelihood    Accuracy')
+        print('      ---------------------------------------')
+
+    # Old log-likelihood and accuracy; used to check if the change
+    # in log-likelihood or accuracy is sufficient to indicate convergence.
[…]

### 2014-07-25 src/statsify.py

@@ -137,3 +137,27 @@ def bi_label_classifier_test(classifier, test_set):
     print "Recall    :\t", recall
     print "Fscore    :\t", fscore
 
+def calculate_fscore(classifier, test_set):
+    cm_raw = {
+            "positive": {"positive": 0, "negative": 0},
+            "negative": {"positive": 0, "negative": 0},
+            }
+    for item, intended_label in test_set:
+        result = classifier.classify(item)
+        cm_raw[result][intended_label] += 1
+    try:
+        precison = cm_raw["positive"]["positive"] / \
+            float(cm_raw["positive"]["positive"] + cm_raw["positive"]["negative"])
+    except:
+        precison = 0.0
+    try:
+        recall = cm_raw["positive"]["positive"] / \
+            float(cm_raw["positive"]["positive"] + cm_raw["negative"]["positive"])
+    except:
+        recall = 0.0
+    try:
+        fscore = 2 * ((precison * recall)/(precison + recall))
+    except:
+        fscore = 0.0
+    return fscore
+

### 2014-07-25 src/train.py

@@ -1,13 +1,10 @@
 #!/usr/bin/env python
 
 import nltk
-import numpy
 import statsify
 
 from nltk.featstruct import FeatStruct
-from nltk.classify.maxent import CutoffChecker, BinaryMaxentFeatureEncoding, calculate_empirical_fcount
-from nltk.classify.maxent import calculate_nfmap, ConditionalExponentialClassifier, log_likelihood, accuracy
-from nltk.classify.maxent import calculate_deltas
+from maxent_classifier_with_validation import train_maxent_classifier_with_validation
 
 class classifier:
     def __init__(self, train_set):
@@ -32,7 +29,7 @@ class classifier:
             print "Should have been:", intended, "Was:", result, error
 
 
-class multi_label_classifier(classifier):
+class maxent_classifier(classifier):
     def __init__(self, train_set, iterations=None, lldelta=None, ll=None):
         if lldelta:
             print "Cutoff after log likelyhood changes by less than", lldelta
@@ -46,111 +43,33 @@ class multi_label_classifier(classifier):
             print "Cutoff after {} iterations".format(iterations)
             self.classifier = nltk.MaxentClassifier.train(train_set, max_iter=iterations)
 
-def train_maxent_classifier_with_iis_with_validation(train_toks, prev_weights=None, trace=3, encoding=None,
-                                     labels=None, **cutoffs):
-    """
-    Derived from train_maxent_classifier_with_iis
-    """
-    cutoffs.setdefault('max_iter', 100)
-    cutoffchecker = CutoffChecker(cutoffs)
 
-    # Construct an encoding from the training data.
-    if encoding is None:
-        encoding = BinaryMaxentFeatureEncoding.train(train_toks, labels=labels)
-
-    # Count how many times each feature occurs in the training data.
-    empirical_ffreq = (calculate_empirical_fcount(train_toks, encoding) /
-                       len(train_toks))
-
-    # Find the nf map, and related variables nfarray and nfident.
-    # nf is the sum of the features for a given labeled text.
-    # nfmap compresses this sparse set of values to a dense list.
-    # nfarray performs the reverse operation.  nfident is
-    # nfarray multiplied by an identity matrix.
-    nfmap = calculate_nfmap(train_toks, encoding)
-    nfarray = numpy.array(sorted(nfmap, key=nfmap.__getitem__), 'd')
-    nftranspose = numpy.reshape(nfarray, (len(nfarray), 1))
-
-    # Check for any features that are not attested in train_toks.
[…]

### 2014-07-25 src/conductor.py
Added options to get a baseline

@@ -36,6 +36,10 @@ def parse_args():
             help="This parameter changes the cutoff for training for max ent ")
     parser.add_argument("--validationMetric", default="none",
             help="This changes the metric for validation set evaluation")
+    parser.add_argument("--no-uncommon-selection", dest="uncommon_selection",
+            action="store_false", help="This toggles whither word selection is on off")
+    parser.add_argument("--no-stopword-removal", dest="stopword_removal",
+            action="store_false", help="This toggles whither stopword removal is on off")
     parser.add_argument("--classifier_type", default="max_ent",
             help="Select classifier should be:" + " ".join(classifier_types))
     parser.add_argument("--labels", default="pn",
@@ -63,8 +67,13 @@ if __name__ == "__main__":
     print "Transforming dataset..."
     feature_list = dictizer.__call__(tokens)
 
-    print "Selecting features from the dataset..."
-    feature_list = wordselection.__call__(feature_list)
+    if args.stopword_removal:
+        print "Removing stopwords from the dataset..."
+        feature_list = wordselection.remove_uncommon(feature_list)
+
+    if args.uncommon_selection:
+        print "Removing uncommon words from the dataset..."
+        feature_list = wordselection.remove_stopwords(feature_list)
 
     print "Splitting the dataset..."
     if args.validationMetric == "none":

### 2014-07-25 src/train.py

@@ -66,7 +66,8 @@ class maxent_classifier_with_validation(classifier):
                 metric = statsify.calculate_fscore(self.classifier, validation_set)
             print "Iteration {} {}  :\t{}".format(iter_count, metric_type, metric)
             print "{} delta  :\t{}".format(metric_type, metric - prev_metric)
-
+        print "Restoring iteration {} weights".format(iter_count-1)
+        self.classifier.set_weights(prev_weights)
 
 
 class naive_bayes_classifier(classifier):

### 2014-07-25 src/wordselection.py

@@ -1,8 +1,8 @@
 #!/usr/bin/env python
 
-# File       : wordselection.py
-# Author     : Douglas Anderson
-# Description: This file removes unnecessary tokens
+# File        : wordselection.py
+# Author      : Douglas Anderson
+# Description : This file removes unnecessary tokens
 
 
 def __call__(input_list):

### 2014-07-25 paper/figures/feature_hist.R
Created a histogram of term frequancies

@@ -1,0 +1,11 @@
+
+library(ggplot2)
+
+data <- read.table("features.tsv", col.names=c("y", "x"), sep="\t")
+
+chart_title <- "Histogram of Term Occurrences"
+xlab <- "Term Rank"
+ylab <- "Document Frequency"
+
+ggplot(data, aes(x)) + geom_histogram(binwidth=0.2) + scale_x_log10(breaks=c(1,2,5,10,100,1000)) + ggtitle(chart_title) + xlab(xlab) + ylab(ylab) + theme_minimal()
+

### 2014-07-25 src/conductor.py

@@ -107,6 +107,6 @@ if __name__ == "__main__":
 
     print "\nTesting"
     classifier.test(test_set, args.labels)
-    #classifier.show_informitive_features()
+    classifier.show_informitive_features()
     #classifier.inspect_errors(test_set)
 

### 2014-07-27 src/conductor.py
Added some flex to the show most informitive features

@@ -107,6 +107,7 @@ if __name__ == "__main__":
 
     print "\nTesting"
     classifier.test(test_set, args.labels)
-    classifier.show_informitive_features()
+
+    #classifier.show_informitive_features(30)
     #classifier.inspect_errors(test_set)
 

### 2014-07-27 src/train.py

@@ -16,8 +16,8 @@ class classifier:
         else:
             statsify.bi_label_classifier_test(self.classifier, test_set)
 
-    def show_informitive_features(self):
-        self.classifier.show_most_informative_features(20)
+    def show_informitive_features(self, numFeatures):
+        self.classifier.show_most_informative_features(numFeatures)
 
     def inspect_errors(self, test_set):
         errors = []

### 2014-07-27 src/conductor.py
Implemeted smoothing. Pretty cool stuff

@@ -75,12 +75,6 @@ if __name__ == "__main__":
         print "Removing uncommon words from the dataset..."
         feature_list = wordselection.remove_stopwords(feature_list)
 
-    print "Splitting the dataset..."
-    if args.validationMetric == "none":
-        train_set, _, test_set = split_dataset.__call__(feature_list, 0.2)
-    else:
-        train_set, validation_set, test_set = split_dataset.__call__(feature_list, 0.2, validation_size=0.2)
-
     # Write the features out to a file
     with open("filtered_docs.txt", "w") as w:
         for row in feature_list:
@@ -89,6 +83,12 @@ if __name__ == "__main__":
     print "Generating feature set statistics..."
     statsify.__call__(feature_list, args.labels)
 
+    print "Splitting the dataset..."
+    if args.validationMetric == "none":
+        train_set, _, test_set = split_dataset.__call__(feature_list, 0.2)
+    else:
+        train_set, validation_set, test_set = split_dataset.__call__(feature_list, 0.2, validation_size=0.2)
+
     if args.classifier_type == "max_ent":
         if args.minlldelta:
             classifier = maxent_classifier(train_set, lldelta=args.minlldelta)
@@ -96,7 +96,7 @@ if __name__ == "__main__":
             classifier = maxent_classifier(train_set, ll=args.minll)
         elif args.validationMetric != "none":
             classifier = maxent_classifier_with_validation(train_set, validation_set,
-                    args.validationMetric)
+                    args.validationMetric, 3)
         elif args.numIterations:
             classifier = maxent_classifier(train_set, iterations=args.numIterations)
         else:

### 2014-07-27 src/train.py

@@ -45,29 +45,39 @@ class maxent_classifier(classifier):
 
 
 class maxent_classifier_with_validation(classifier):
-    def __init__(self, train_set, validation_set, metric_type):
+    def __init__(self, train_set, validation_set, metric_type, smoothing):
         self.classifier = nltk.MaxentClassifier.train(train_set, trace=1, max_iter=5)
         iter_count = 0
+        rounds_without_improvment = 0
         if metric_type == "accuracy":
             metric = nltk.classify.accuracy(self.classifier, validation_set)
         else:
             metric = statsify.calculate_fscore(self.classifier, validation_set)
-        prev_metric = 0.0
+        best_iteration = 0
+        best_metric = metric
+        best_weights = self.classifier.weights()
         print "Iteration {} {}  :\t{}".format(iter_count, metric_type, metric)
-        while (metric - prev_metric) > 0.0:
+        #while (metric - prev_metric) >= 0.0:
+        while rounds_without_improvment < smoothing:
             iter_count += 1
-            prev_weights = self.classifier.weights()
             self.classifier = train_maxent_classifier_with_validation(train_set,
-                    trace=1, prev_weights=prev_weights, max_iter=1)
-            prev_metric = metric
+                    trace=1, prev_weights=self.classifier.weights(), max_iter=1)
             if metric_type == "accuracy":
                 metric = nltk.classify.accuracy(self.classifier, validation_set)
             else:
                 metric = statsify.calculate_fscore(self.classifier, validation_set)
             print "Iteration {} {}  :\t{}".format(iter_count, metric_type, metric)
-            print "{} delta  :\t{}".format(metric_type, metric - prev_metric)
-        print "Restoring iteration {} weights".format(iter_count-1)
-        self.classifier.set_weights(prev_weights)
+            print "{} delta  :\t{}".format(metric_type, metric - best_metric)
+            if(metric - best_metric) <= 0.0:
+                rounds_without_improvment += 1
+            else:
+                rounds_without_improvment = 0
+                best_iteration = iter_count
+                best_metric = metric
+                best_weights = self.classifier.weights()
+
+        print "Restoring iteration {} weights".format(best_iteration)
+        self.classifier.set_weights(best_weights)
 
 
 class naive_bayes_classifier(classifier):

### 2014-07-28 paper/paper.tex
Fixed the second reader's name. Hopefully.
Wrote much of the introduction. It's not the best but it could be much worse

@@
 
-Professor Lee % TODO which professor Lee?
+Professor Xining Li
 
@@
 
+A great deal of modern communications technologies allow people to discuss and
+disseminate their opinions with a near negligible cost. Since the extremely low
+cost allows everyone to share their opinions, the scale of textual data is
+enormous. In order to gain insight into the `overall' opinion on particular
+topics, the process of determining sentiment must be automated.
+
 \subsection{Topic Area}
+
+Sentiment analysis is simply a classification task that attempts to label
+fragments of text with a label that appropriately summarizes the attitude of
+the text. Natural Language Processing (NLP) provides a number of method for
+preforming sentiment analysis. Many of these methods take a probabilistic
+approach to performing the task.
+
+%TODO how could this be useful
+
 \subsection{Specific Problem}
+
+The focus of this undergraduate research project has been to preform sentiment
+analysis in data from the microbloging website Twitter. This data presents some
+interesting problems to performing good sentiment analysis due to it's short
+and informal nature. All of the messages, known as Tweets, are constrained in
+length to 140 characters. This limit forces many users of Twitter to use
+abbreviations and contractions. Twitter makes it extremely easy to publish a
+Tweet and has no way to edit a Tweet once published. This results more spelling
+and grammar mistakes then other sources of text. Tweets often also contain
+links to other websites in the form of URLs as well as taging system for topics
+and other users.
+
 \subsection{Task Description}
+
+Organizers of the SemEval-2013 workshop created various sentiment analysis
+tasks to be preformed. The task focused on for this project was task-2b:
+Message polarity classification. The organizers used the amazon service
+``Mechanical Turk" to get many humans to annotate Tweets as `positive',
+`negative' or `neutral'. In tweets with mixed sentiments the prevailing
+sentiment was chosen. Participants were tasked with creating a classifier to
+establish labels for Tweets not in the training dataset. The various
+submissions of the participants were then evaluated by the average of the
+F-positive and the F-negative.
 

### 2014-07-28 paper/paper.tex
Added the biginnings of a bibliography to the paper
Added most of the documents that I read for the bibliography. Also Started on the approch

@@
 \usepackage{setspace}
+\usepackage[numbers]{natbib}
 
@@
 
+Quite a bit of research has been done in the field of sentiment analysis
+recently. Much of the work has involved data from other contexts such as Movie
+reviews \cite{Pang2002}, and blog posts \cite{Melville2009}. The challenges
+associated with classifying Twitter data has attracted researchers in the past
+few years \cite{Jianfeng2013} \cite{Barbosa2010} \cite{Gokulakrishnan2012}.
+
 \section{Approach}
+
+The Maximum Entropy classification method that was focused on due to the
+limited duration of the project. This supervised machine learning method
+calculates the probability that a given document $d$ belongs to the class $c$.
+
+The maximum entropy approach is well described in \cite{Pang2002} and
+\cite{Nigam1999} and is summarized below.
+
+\begin{equation}
+    P(c | d) = \frac{1}{Z(d)} exp( \sum\limits_{i} \lambda _{i,c} F_{i,c}(d,c) )
+\end{equation}
+
+Where $Z(d)$ is a normalization function. $F_{i,c}$ is a feature function for
+feature $f_{i}$ and class $c$.
 
@@
 
+\nocite{*}
+\bibliographystyle{ieeetr}
+\bibliography{paper}
+
 \end{document}

### 2014-07-29 paper/paper.tex
Wrote a whole bunch for implementation

@@
 
+\subsection{Summary of Maximum Entropy}
+
 The Maximum Entropy classification method that was focused on due to the
@@
 
-The maximum entropy approach is well described in \cite{Pang2002} and
-\cite{Nigam1999} and is summarized below.
+The maximum entropy approach is well described in \cite{Nigam1999} and is
+summarized below. The training data is used to establish constraints in the
+following fashion.
 
@@
 
-Where $Z(d)$ is a normalization function. $F_{i,c}$ is a feature function for
-feature $f_{i}$ and class $c$.
+Where $Z(d)$ is a normalization function, $F_{i,c}$ is a feature function for
+feature $f_{i}$ and class $c$, and $\lambda_{i}$ is a feature parameter.
+
+In order to establish reasonable $\lambda_{i}$ for each feature the Improved
+Iterative Scaling is employed.
+
+%TODO outline the IIS algorithm
+
+\subsection{Implementation}
+
+The classifier produced for this project is implemented in \textit{python} and make
+extensive use of the \textit{nltk} (Natural Language Toolkit) library.
+
+\begin{enumerate}
+
+    \item \textbf{Tokenization} - The text is read into memory and separated into
+        tokens. Each token represents an atom of text. Token types include
+        word, number, user, hashtag, url, emoticon and punctuation.
+
+    \item \textbf{Normalizing} - Each token is simplified to assist in
+        classification by reducing the number of tokens.
+
+        \begin{itemize}
+
+            \item \textbf{Words} are coerced into lowercase
+
+            \item \textbf{Numbers} are replaced with "\#NUM"
+
+            \item \textbf{User} are replaced with "@USER"
+
+            \item \textbf{Hashtags} are replaced with "\#OCTOTHORPE"
+
+            \item \textbf{URLs} are replaced with "@URL"
+
+            \item \textbf{Emoticon} are grouped into four different groups
+                based on their intended meaning. Each group is then replaced
+                with a representation. (e.g. `:)' $\rightarrow$ `EM\_HAPPY' and
+                `;-p' $\rightarrow$ `EM\_WINK')
+
+            \item most \textbf{Punctuation} is replaced with "PUNCT" however
+                question marks, punctuation marks, and ellipsis are each
+                replaced with their own representation.
+
+        \end{itemize}
+
+    \item \textbf{Feature Selection} - The number of tokens retained as
+        features is further reduced.
+        \begin{itemize}
+
+            \item By \textbf{Removing Stopwords}, words that do not
+                discriminate between classes are eliminated. Because of the
+                limited size of the dataset only 28 stopwords are used.
+
+            \item Then \textbf{Uncommon words} are removed. Words that do not
+                meet a certain document frequency threshold are eliminated.
+                Many of these words are proper nouns that, if retained are
+                likely to cause the classifier to overfit to the training set
+
+        \end{itemize}
+
+    \item \textbf{Training}
+    \item \textbf{Testing}
+\end{enumerate}
 

### 2014-07-29 src/normalize.py

@@ -73,3 +73,4 @@ def normalize_words(tokens):
     for t in tokens:
         if t.tokentype == "word":
             t.text = t.text.lower()
+

### 2014-07-29 paper/paper.tex
Wrote more things

@@
                 Many of these words are proper nouns that, if retained are
-                likely to cause the classifier to overfit to the training set
+                likely to cause the classifier to overfit to the training set.
 
@@
 
-    \item \textbf{Training}
-    \item \textbf{Testing}
+    \item \textbf{Splitting} - The corpus of documents are random separated
+        into three sets: the \textit{training set}, the \textit{validation set},
+        and the \textit{testing set}. Respectively, Each dataset is 60\%, 20\%,
+        and 20\% of the corpus.
+
+    \item \textbf{Training} -
+
+    \item \textbf{Testing} - The performance of the dataset is evaulated
+        against the \textit{testing set}.
+
 \end{enumerate}

### 2014-07-29 paper/paper.tex
Wrote a section explaing the use of the validation set and a section for futre work

@@
 limited duration of the project. This supervised machine learning method
-calculates the probability that a given document $d$ belongs to the class $c$.
+calculates the probability that a given document $d$ belongs to the class $c$. The maximum entropy approach is well described in \cite{Nigam1999} and is summarized below.
 
-The maximum entropy approach is well described in \cite{Nigam1999} and is
-summarized below. The training data is used to establish constraints in the
-following fashion.
+The training data is used to establish constraints in the following fashion.
 
 \begin{equation}
-    P(c | d) = \frac{1}{Z(d)} exp( \sum\limits_{i} \lambda _{i,c} F_{i,c}(d,c) )
+    P(c | d) = \frac{1}{Z(d)} \mathrm{exp}(\sum\limits_{i} \lambda _{i,c} F_{i,c}(d,c) )
 \end{equation}
@@
 In order to establish reasonable $\lambda_{i}$ for each feature the Improved
-Iterative Scaling is employed.
+Iterative Scaling (IIS) is employed. Given a set of training data
+$\mathcal{D}$, IIS trains a model $\Lambda$ by performing a hillclimbing procedure with the function $l(\Lambda|\mathcal{D})$, where:
 
-%TODO outline the IIS algorithm
+\begin{equation}
+    l(\Lambda | \mathcal{D}) = \sum\limits_{d\in\mathcal{D}} \sum\limits_{i}
+    \lambda_{i} f_{i}(d,c(d)) - \sum\limits_{d\in\mathcal{D}} \mathrm{log}
+    \sum\limits_{c} \mathrm{exp} \sum\limits_{i} \lambda_{i} f_{i}(d,c)
+\end{equation}
+
+Starting with any initial vector of parameters $\Lambda$, at each iteration
+we improve the parameters by setting $\Lambda = \Lambda + \Delta$.
 
@@
 
-    \item \textbf{Training} -
+    \item \textbf{Training} - The classifier is trained using the
+        \textit{training set}.  The classifier uses the \textit{validation set}
+        to evaluate the training process and attempt to curtail overfitting.
 
-    \item \textbf{Testing} - The performance of the dataset is evaulated
+    \item \textbf{Testing} - The performance of the dataset is evaluated
         against the \textit{testing set}.
@@
 
+\subsection{Baseline}
+
+\subsection{Avoiding overfitting}
+
+The implementation created for this project used a validation set during
+training as the primary mechanism to avoid overfitting. While training the
+effectiveness of the classifier was evaluated after every iteration, using the
+accuracy or F-positive measure. During the training process the following
+procedure was followed:
+
+\begin{enumerate}
+
+    \item The classifier was trained for 5 iterations to establish reasonable
+        initial weights.
+
+    \item Evaluate the classifier using the validation set. Like the
+        \textit{testing set} that will evaluate the classifiers final
+        performance, the \textit{validation set} shares no common examples with
+        the \textit{training set} and will therefore give a reasonable
+        indication of how the classifier will perform with unseen examples.
+
+    \item Repeat the following until performance degrades for a specified
+        number of iterations
+
+    \begin{enumerate}
+
+        \item Train the classifier for another iteration.
+
+        \item Evaluate performance with the \textit{validation set}.
+
+    \end{enumerate}
+
+    \item Restore the $\Lambda$ value of the best performing iteration.
+
+\end{enumerate}
+
 \section{Conclusion}
@@
 
-\section{Works Cited}
+\subsection{Hashtags}
+
+\subsection{Users}
+
+Nearly all Twitter users have published more than one tweet. A more advanced
+classifier could establish a particular users propensity to publishing a
+prevailing sentiment in all of their tweets.
+
+As well, some Twitter users may be frequently be referred to with a particular
+sentiment. For a hypothetical example, Tweets addresses to Emma Watson
+(`@EmWatson') are more likely to have a positive sentiment, while tweets to
+Barack Obama (`@BarackObama') may contain extremely mixed sentiment.
+
+% Bibliography
 

### 2014-07-29 paper/paper.tex
Wrote a future work section for hashtags

@@
 
+%TODO extend
+
 \section{Approach}
@@
 
+After the SemEval-2013 workshop the organizers released a paper discussing the
+proceedings and the results of the task.
+
+%TODO
+
 \subsection{Avoiding overfitting}
@@
 
+Hashtags are a way that Twitter users tag a Tweet as part of a particular
+conversation. Hashtags refer to proper nouns such as events, places, or people.
+Hashtags can also denote modifiers (such as `\#sarcasm') to the sentiment of the
+Tweet, or even raw sentiment (e.g. `\#yay').
+
+While it is likely infeasible to retain Hashtags about proper nouns,
+classification performance could be improved by including modifiers and
+Hashtags with raw sentiment. The following Tweet (not from the dataset) is a
+great example of a Tweet that Hashtags could help improve classification
+accuracy.
+
+\begin{verbatim}
+    Well I have an ear infection #good #sarcasm
+\end{verbatim}
+
+While a simple approach could be to strip the octothorpe from the front of the
+Hashtag (e.g. `\#good' $\rightarrow$ `good'), the semantic meaning of the two
+are different. Hashtags often have message level meaning while simple words
+have local context withing the sentence. Since the dataset created for the
+SemEval-2013 workshop mostly contained examples of Hashtags used as proper
+nouns, more annotated Tweets would be needed for training and testing.
+
 \subsection{Users}
@@
 
+A challenge that this method could introduce is the introduction of a temporal
+element since people's outlooks, and therefore sentiment's in Tweets, will
+change over time. As well as public perception of a individual changes, the
+prevailing sentiment my change as well.
+
 % Bibliography

### 2014-07-29 paper/paper.tex
Wrote a bit for the baseline measure

@@
 
-A great deal of modern communications technologies allow people to discuss and
-disseminate their opinions with a near negligible cost. Since the extremely low
-cost allows everyone to share their opinions, the scale of textual data is
-enormous. In order to gain insight into the `overall' opinion on particular
-topics, the process of determining sentiment must be automated.
+Social Media allows people to discuss topics and disseminate their opinions
+with a near negligible cost. Since the cost of using social media is so low it
+allows everyone to share their opinions as much as they please. Because of this
+the scale of textual data is enormous. In order to gain insight into the
+`overall' opinion on particular topics, the process of determining sentiment
+must be automated.
 
@@
 the text. Natural Language Processing (NLP) provides a number of method for
-preforming sentiment analysis. Many of these methods take a probabilistic
-approach to performing the task.
+preforming sentiment analysis. Many of these methods, such as Naive Bayes and
+Maximum Entropy, take a probabilistic approach to performing the task. Another
+commonly used method of performing sentiment analysis is the uses of a support
+vector machine (SVM).
 
-%TODO how could this be useful
+Performing sentimetn
 
@@
 limited duration of the project. This supervised machine learning method
-calculates the probability that a given document $d$ belongs to the class $c$. The maximum entropy approach is well described in \cite{Nigam1999} and is summarized below.
+calculates the probability that a given document $d$ belongs to the class $c$.
+The maximum entropy approach is well described in \cite{Nigam1999} and is
+summarized below.
 
@@
 Iterative Scaling (IIS) is employed. Given a set of training data
-$\mathcal{D}$, IIS trains a model $\Lambda$ by performing a hillclimbing procedure with the function $l(\Lambda|\mathcal{D})$, where:
+$\mathcal{D}$, IIS trains a model $\Lambda$ by performing a hillclimbing
+procedure with the function $l(\Lambda|\mathcal{D})$, where:
 
@@
 
-The classifier produced for this project is implemented in \textit{python} and make
-extensive use of the \textit{nltk} (Natural Language Toolkit) library.
+The classifier produced for this project is implemented in \textit{python} and
+make extensive use of the \textit{nltk} (Natural Language Toolkit) library. As
+well the implementation makes use of the \textit{flex} tool to create a lexer
+for tokenization.
 
@@
 
-\section{Discussion}
-
-\subsection{Baseline}
-
-After the SemEval-2013 workshop the organizers released a paper discussing the
-proceedings and the results of the task.
-
-%TODO
-
 \subsection{Avoiding overfitting}
@@
 
+\section{Discussion}
+
+\subsection{Baseline}
+
+After the SemEval-2013 workshop the organizers released a paper discussing the
+proceedings and the results of the task \cite{Nakov2013}. The paper establishes
+baseline in terms of $F$. $F$ can be calculated $F = (F_{pos} + F_{neg}) / 2$
+where $F_{pos} = 2 \frac{P_{pos}R_{pos}}{P_{pos} + R_{pos}}$ and $F_{neg}$ is
+calculated in a similar fashion. The Precision measure for the positive label
+is $P_{pos} = \frac{\mathrm{\# of\ true\ postive}}{\mathrm{\# of\ true\
+postive} + \mathrm{\# of\ false\ postive} }$. The Recall measure for the
+positive label is defined as $R_{pos} = \frac{\mathrm{\# of\ true\
+postive}}{\mathrm{\# of\ true\ postive} + \mathrm{\# of\ false\ negative} }$
+
+%TODO note that my solution is unconstrained
+
+\subsection{Results}
+
+\subsection{Comparison to Workshop Participants}
+
+Table \ref{table:comparison} shows the performance of the classifier produced
+for this project ranks compared to results of the workshop participants. The
+full table (with out this project's results) can be found in table 9 of Nakov
+et al. \cite{Nakov2013}.
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{|r|l|}
+        \hline
+        Run & F \\
+        \hline
+        NRC-Canada & 69.02 \\
+        GU-MLT-LT  & 65.27 \\
+        teragram   & 64.86 \\
+        BOUNCE     & 63.53 \\
+        KLUE       & 63.06 \\
+        \hline
+    \end{tabular}
+    \end{center}
+    \caption{Comparison of unconstrained classifiers by F-score}
+    \label{table:comparison}
+\end{table}
+
+%TODO finsh table
+
 \section{Conclusion}
+
+I am great and without reproach.
+
+%TODO get a stronger conclusion
 
@@
 
+As well Hashtags sometimes use CamelCase to create multi-word tags (e.g.
+`\#SorryNotSorry'). It could prove worthwhile to attempt the decompose
+CamelCase Hashtags into its component words during feature selection.
+
 \subsection{Users}

### 2014-07-29 paper/paper.tex
Wrote some more scattered things

@@
 
-Utilizing maximum entropy classifiers for sentiment analysis in twitter messages
+Utilizing Maximum Entropy classification for sentiment analysis in twitter
+messages
 
@@
 
-August 1, 2014 %TODO fix this
+July 29th, 2014 %TODO fix this
 
@@
 Professor Xining Li
+
+\vspace{1.5cm}
+
+Draft 1 %TODO ditch this
 
@@
 
-Performing sentimetn
+Performing sentiment analysis is becoming a very important field of study for
+many businesses. If a company can determine what consumers think of their
+products they can take actions such as improve their products or appease an
+unsatisfied customer.
 
@@
 submissions of the participants were then evaluated by the average of the
-F-positive and the F-negative.
+F-positive and the F-negative. The submissions were allowed categorized as
+`unconstrained' or `constrained' depending on if they did or did not use
+supplemental data, respectively.
 
@@
 few years \cite{Jianfeng2013} \cite{Barbosa2010} \cite{Gokulakrishnan2012}.
+Many previous attempts researched make use of Native Bayes, Maximum Entropy,
+and SVM classifiers.
 
@@
 well the implementation makes use of the \textit{flex} tool to create a lexer
-for tokenization.
+for tokenization. The classifier does not make uses of any supplemental
+datasets and therefore should be considered constrained within the context of
+the task.
 
@@
 
-\subsection{Baseline}
+\subsection{Evaluation Method}
 
@@
 %TODO note that my solution is unconstrained
+
+\subsection{Baseline}
 
@@
         \hline
+        Majority Baseline & 29.19 \\
+        \hline
     \end{tabular}
     \end{center}
-    \caption{Comparison of unconstrained classifiers by F-score}
+    \caption{Comparison of constrained classifiers by F-score.}
     \label{table:comparison}
@@
 % Bibliography
-
 \nocite{*}

### 2014-07-29 src/labelselect.py
Rewrote most of the evaluation. Starting to get results that are indicating that naive bayes does not perform better then max ent... Not really the results I wanted. At least my results are better than some of the teams in the workshop

@@ -19,6 +19,9 @@ def selectPosNeuNeg(tokens):
             selected_tokens.append(t)
         elif t.label == "neutral":
             selected_tokens.append(t)
+        elif t.label == "objective" or t.label == "objective-OR-neutral":
+            t.label = "neutral" # Coerce the labels to neutral
+            selected_tokens.append(t)
         elif t.label == "negative":
             selected_tokens.append(t)
     return selected_tokens
@@ -31,3 +34,4 @@ def selectPosNeg(tokens):
         elif t.label == "negative":
             selected_tokens.append(t)
     return selected_tokens
+

### 2014-07-29 src/statsify.py

@@ -19,8 +19,6 @@ def __call__(feature_list, labels):
     if labels == "pnn":
         print "% neutral  :", num_neu_docs / float(num_docs)
     print "% negative :", num_neg_docs / float(num_docs)
-    #print "Number of training documents:", len(train_set)
-    #print "Number of test documents:", len(test_set)
 
     num_features = 0
     num_pos_features = 0
@@ -43,121 +41,90 @@ def __call__(feature_list, labels):
         print "Avg neutral  / doc :", num_neu_features / float(num_neu_docs)
     print "Avg negative / doc :", num_neg_features / float(num_neg_docs)
 
-def print_multi_confusion_matrix(cc):
+def print_multi_confusion_matrix(cm):
+    pos = "positive"
+    neu = "neutral"
+    neg = "negative"
     print "\n   \tpos\tneu\tneg"
-    print "pos\t",cc["positive"]["positive"],"\t",cc["positive"]["neutral"],"\t",cc["positive"]["negative"]
-    print "neu\t",cc["neutral"]["positive"],"\t",cc["neutral"]["neutral"],"\t",cc["neutral"]["negative"]
-    print "neg\t",cc["negative"]["positive"],"\t",cc["negative"]["neutral"],"\t",cc["negative"]["negative"]
+    print "pos\t",cm[pos][pos],"\t",cm[pos][neu],"\t",cm[pos][neg]
+    print "neu\t",cm[neu][pos],"\t",cm[neu][neu],"\t",cm[neu][neg]
+    print "neg\t",cm[neg][pos],"\t",cm[neg][neu],"\t",cm[neg][neg]
 
-def print_bi_confusion_matrix(cc):
+def print_bi_confusion_matrix(cm):
     print "\n   \tpos\tneg"
-    print "pos\t",cc["positive"]["positive"],"\t",cc["positive"]["negative"]
-    print "neg\t",cc["negative"]["positive"],"\t",cc["negative"]["negative"]
+    print "pos\t",cm["positive"]["positive"],"\t",cm["positive"]["negative"]
+    print "neg\t",cm["negative"]["positive"],"\t",cm["negative"]["negative"]
 
-def calculate_confusion_matrix(cc):
-    label_stats = {
-            "positive": {"tp": 0, "tn": 0, "fp": 0, "fn": 0},
-            "neutral":  {"tp": 0, "tn": 0, "fp": 0, "fn": 0},
[…]

### 2014-07-29 src/train.py

@@ -11,10 +11,7 @@ class classifier:
         pass
 
     def test(self, test_set, labels):
-        if labels == "pnn":
-            statsify.multi_label_classifier_test(self.classifier, test_set)
-        else:
-            statsify.bi_label_classifier_test(self.classifier, test_set)
+        statsify.calculate_fscore(self.classifier, test_set, trace=True)
 
     def show_informitive_features(self, numFeatures):
         self.classifier.show_most_informative_features(numFeatures)
@@ -52,7 +49,7 @@ class maxent_classifier_with_validation(classifier):
         if metric_type == "accuracy":
             metric = nltk.classify.accuracy(self.classifier, validation_set)
         else:
-            metric = statsify.calculate_fscore(self.classifier, validation_set)
+            metric = statsify.calculate_fscore(self.classifier, validation_set, trace=False)
         best_iteration = 0
         best_metric = metric
         best_weights = self.classifier.weights()
@@ -65,7 +62,7 @@ class maxent_classifier_with_validation(classifier):
             if metric_type == "accuracy":
                 metric = nltk.classify.accuracy(self.classifier, validation_set)
             else:
-                metric = statsify.calculate_fscore(self.classifier, validation_set)
+                metric = statsify.calculate_fscore(self.classifier, validation_set, trace=False)
             print "Iteration {} {}  :\t{}".format(iter_count, metric_type, metric)
             print "{} delta  :\t{}".format(metric_type, metric - best_metric)
             if(metric - best_metric) <= 0.0:

### 2014-07-30 paper/paper.tex
Extended the results table. Added the beginnings of a results table. About to get meg to look at what I have so far

@@
 
-%TODO note that my solution is unconstrained
-
 \subsection{Baseline}
 
+TODO establish baseline here
+
 \subsection{Results}
+
+Since the \textit{test set} is random subset of the corpus, the results of the
+classifier can vary slightly between runs. In order to effectively evaluate the
+performance of the classifier under certain conditions each experiment is
+conducted 3 times and averaged.
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{|c|c|r|r|r|r|}
+        \hline
+        Description & Stopwords & Run 1 & Run 2 & Run 3 & $\mu$ F\\
+        \hline
+        MaxEnt      & Yes       & 0.0   & 0.0   & 0     & 0 \\
+        \dots       & No        & 0.0   & 0.0   & 0     & 0 \\
+        Naive Bayes & Yes       & 0.0   & 0.0   & 0     & 0 \\
+        \dots       & No        & 0.0   & 0.0   & 0     & 0 \\
+        \hline
+    \end{tabular}
+    \end{center}
+    \caption{Results of variations on feature selection and training. Sorted by
+        average F-score.}
+    \label{table:results}
+\end{table}
 
@@
 Table \ref{table:comparison} shows the performance of the classifier produced
-for this project ranks compared to results of the workshop participants. The
-full table (with out this project's results) can be found in table 9 of Nakov
-et al. \cite{Nakov2013}.
+for this project compared to results of the workshop participants. The full
+table (with out this project's results) can be found in table 9 of Nakov et al.
+\cite{Nakov2013}.
 
@@
         \hline
-        Run & F \\
+        Team & F \\
         \hline
@@
         KLUE       & 63.06 \\
+        AMI\&ERIC  & 62.55 \\
+        FBM        & 61.17 \\
+        AVAYA      & 60.84 \\
+        SAIL       & 60.14 \\
+        UT-DB      & 59.87 \\
+        FBK-irst   & 59.76 \\
+        nlp.cs.aueb.gr & 58.91 \\
+        UNITOR     & 58.27 \\
+        LVIC-LIMSI & 57.14 \\
+        Unigon     & 56.96 \\
+        NILC\_USP   & 56.31 \\
+        DataMining & 55.52 \\
+        ECNUCS     & 55.05 \\
+        nlp.cs.aueb.gr & 54.73 \\
+        ASVUniOfLeipzig & 54.56 \\
+        SZTE-NLP   & 54.33 \\
+        CodeX      & 53.89 \\
+        Oasis      & 53.84 \\
+        \textbf{Best MaxEnt}& \textbf{53.32} \\
+        NTNU       & 53.23 \\
+        UoM        & 51.81 \\
+        SSA-UO     & 50.17 \\
+        SenselyticTeam & 50.10 \\
+        $\ldots$ & $\ldots$ \\
+        9 more teams &  \textless\ 50 \\
+        $\ldots$ & $\ldots$ \\
         \hline
@@
     \end{center}
-    \caption{Comparison of constrained classifiers by F-score.}
+    \caption{Comparison of constrained classifiers sumitted to the SemEval-2013
+        workshop. Sorted by F-score.}
     \label{table:comparison}
 \end{table}
-
-%TODO finsh table
 

### 2014-07-30 paper/paper.tex
Made Meg's edits and upped the draft number

@@
 
-Utilizing Maximum Entropy classification for sentiment analysis in twitter
-messages
+Utilizing Maximum Entropy Classification for Sentiment Analysis in Twitter
+Messages
 
@@
 
-Draft 1 %TODO ditch this
+Draft 2 %TODO ditch this
 
@@
 \newpage
-\pagestyle{headings}
+%\pagestyle{headings}
 \setcounter{page}{1}
@@
 
-Social Media allows people to discuss topics and disseminate their opinions
-with a near negligible cost. Since the cost of using social media is so low it
-allows everyone to share their opinions as much as they please. Because of this
-the scale of textual data is enormous. In order to gain insight into the
-`overall' opinion on particular topics, the process of determining sentiment
-must be automated.
-
-\subsection{Topic Area}
-
-Sentiment analysis is simply a classification task that attempts to label
-fragments of text with a label that appropriately summarizes the attitude of
-the text. Natural Language Processing (NLP) provides a number of method for
-preforming sentiment analysis. Many of these methods, such as Naive Bayes and
-Maximum Entropy, take a probabilistic approach to performing the task. Another
-commonly used method of performing sentiment analysis is the uses of a support
-vector machine (SVM).
+Social media allows people to discuss topics and disseminate their opinions
+with a near negligible cost. The low barrier of entry to social media allows
+everyone to share their opinions as much as they please. The scale of textual
+data from social media is enormous. In order to gain insight into the `overall'
+opinion on particular topics, the process of determining sentiment must be
+automated.
 
@@
 
+\subsection{Topic Area}
+
+Sentiment analysis is simply a classification task that attempts to label
+fragments of text that appropriately summarizes the attitude of the text.
+Natural Language Processing (NLP) provides a number of method for preforming
+sentiment analysis. Many of these methods, such as Naive Bayes and Maximum
+Entropy, take a probabilistic approach to performing the task. Another commonly
+used method of performing sentiment analysis is the uses of a support vector
+machine (SVM).
+
 \subsection{Specific Problem}
@@
 The focus of this undergraduate research project has been to preform sentiment
-analysis in data from the microbloging website Twitter. This data presents some
-interesting problems to performing good sentiment analysis due to it's short
-and informal nature. All of the messages, known as Tweets, are constrained in
-length to 140 characters. This limit forces many users of Twitter to use
-abbreviations and contractions. Twitter makes it extremely easy to publish a
-Tweet and has no way to edit a Tweet once published. This results more spelling
-and grammar mistakes then other sources of text. Tweets often also contain
-links to other websites in the form of URLs as well as taging system for topics
-and other users.
+analysis in data from the microbloging website Twitter. All of the messages,
+known as Tweets, are constrained in length to 140 characters. This limit forces
+many users of Twitter to use abbreviations and contractions. This data presents
+some interesting problems to performing good sentiment analysis due to it's
+short and informal nature. Twitter makes it extremely easy to publish a Tweet
+and has no way to edit a Tweet once published. This results in more spelling
+mistakes and inconsistent grammar then other sources of text. Tweets often also
+contain links to other websites in the form of URLs as well as taging system
+for topics and other users.
 
@@
 tasks to be preformed. The task focused on for this project was task-2b:
-Message polarity classification. The organizers used the amazon service
+Message polarity classification. The organizers used the Amazon service
 ``Mechanical Turk" to get many humans to annotate Tweets as `positive',
-`negative' or `neutral'. In tweets with mixed sentiments the prevailing
+`negative' or `neutral'. In tweets with mixed sentiments, the prevailing
 sentiment was chosen. Participants were tasked with creating a classifier to
@@
 
+\textit{Note: This section needs to be expanded. I am just not sure what else to write about...}
+
 %TODO extend
@@
 
-The Maximum Entropy classification method that was focused on due to the
-limited duration of the project. This supervised machine learning method
-calculates the probability that a given document $d$ belongs to the class $c$.
-The maximum entropy approach is well described in \cite{Nigam1999} and is
-summarized below.
+The Maximum Entropy classification method was focused on due to the limited
+duration of the project. This supervised machine learning method calculates the
+probability that a given document $d$ belongs to the class $c$.  The Maximum
+Entropy approach is summarized below. For a more detailed description, see:
+Nigam et al. \cite{Nigam1999}.
 
-The training data is used to establish constraints in the following fashion.
+The training data is used to establish constraints in the following fashion:
 
@@
 
-Where $Z(d)$ is a normalization function, $F_{i,c}$ is a feature function for
+where $Z(d)$ is a normalization function, $F_{i,c}$ is a feature function for
 feature $f_{i}$ and class $c$, and $\lambda_{i}$ is a feature parameter.
@@
 datasets and therefore should be considered constrained within the context of
-the task.
+the task. The classifier adheres to the following procedure:
 
@@
         into three sets: the \textit{training set}, the \textit{validation set},
-        and the \textit{testing set}. Respectively, Each dataset is 60\%, 20\%,
+        and the \textit{testing set}. Respectively, each dataset is 60\%, 20\%,
         and 20\% of the corpus.
@@
 
-The implementation created for this project used a validation set during
+The implementation created for this project used a \textit{validation set} during
 training as the primary mechanism to avoid overfitting. While training the
@@
 where $F_{pos} = 2 \frac{P_{pos}R_{pos}}{P_{pos} + R_{pos}}$ and $F_{neg}$ is
-calculated in a similar fashion. The Precision measure for the positive label
-is $P_{pos} = \frac{\mathrm{\# of\ true\ postive}}{\mathrm{\# of\ true\
-postive} + \mathrm{\# of\ false\ postive} }$. The Recall measure for the
-positive label is defined as $R_{pos} = \frac{\mathrm{\# of\ true\
-postive}}{\mathrm{\# of\ true\ postive} + \mathrm{\# of\ false\ negative} }$
+calculated in a similar fashion. The \textit{Precision} measure for the
+positive label is $P_{pos} = \frac{\mathrm{\# of\ true\ postive}}{\mathrm{\#
+of\ true\ postive} + \mathrm{\# of\ false\ postive} }$. The \textit{Recall}
+measure for the positive label is defined as $R_{pos} = \frac{\mathrm{\# of\
+true\ postive}}{\mathrm{\# of\ true\ postive} + \mathrm{\# of\ false\ negative}
+}$
 
@@
 As well, some Twitter users may be frequently be referred to with a particular
-sentiment. For a hypothetical example, Tweets addresses to Emma Watson
+sentiment. For a hypothetical example, Tweets addressed to Emma Watson
 (`@EmWatson') are more likely to have a positive sentiment, while tweets to

### 2014-07-30 src/conductor.py
Made the normalization optional

@@ -36,10 +36,26 @@ def parse_args():
             help="This parameter changes the cutoff for training for max ent ")
     parser.add_argument("--validationMetric", default="none",
             help="This changes the metric for validation set evaluation")
+
     parser.add_argument("--no-uncommon-selection", dest="uncommon_selection",
             action="store_false", help="This toggles whither word selection is on off")
     parser.add_argument("--no-stopword-removal", dest="stopword_removal",
             action="store_false", help="This toggles whither stopword removal is on off")
+    parser.add_argument("--no-normalize-words", dest="normalize_words",
+            action="store_false", help="This toggles whither words are normalized")
+    parser.add_argument("--no-normalize-punct", dest="normalize_punct",
+            action="store_false", help="This toggles whither words are normalized")
+    parser.add_argument("--no-normalize-emoticons", dest="normalize_emoticons",
+            action="store_false", help="This toggles whither words are normalized")
+    parser.add_argument("--no-normalize-users", dest="normalize_users",
+            action="store_false", help="This toggles whither users are normalized")
+    parser.add_argument("--no-normalize-hashtags", dest="normalize_hashtags",
+            action="store_false", help="This toggles whither hashtags are normalized")
+    parser.add_argument("--no-normalize-nums", dest="normalize_nums",
+            action="store_false", help="This toggles whither nums are normalized")
+    parser.add_argument("--no-normalize-urls", dest="normalize_urls",
+            action="store_false", help="This toggles whither urls are normalized")
+
     parser.add_argument("--classifier_type", default="max_ent",
             help="Select classifier should be:" + " ".join(classifier_types))
     parser.add_argument("--labels", default="pn",
@@ -62,7 +78,21 @@ if __name__ == "__main__":
     tokens = labelselect.__call__(tokens, args.labels) # Select only the labels
 
     print "Normalizing dataset..."
-    tokens = normalize.__call__(tokens) # Normalize the tokens
+    #tokens = normalize.__call__(tokens) # Normalize the tokens
+    if args.normalize_words:
+        normalize.normalize_words(tokens)
+    if args.normalize_punct:
+        normalize.normalize_punct(tokens)
+    if args.normalize_emoticons:
+        normalize.normalize_emoticons(tokens)
+    if args.normalize_users:
+        normalize.normalize_users(tokens)
+    if args.normalize_hashtags:
+        normalize.normalize_hashtags(tokens)
+    if args.normalize_nums:
[…]

### 2014-07-30 src/normalize.py

@@ -8,7 +8,7 @@ import re
 
 def __call__(tokens):
     normalize_words(tokens)
-    normalize_ellipsis(tokens)
+    normalize_punct(tokens)
     normalize_emoticons(tokens)
     normalize_users(tokens)
     normalize_hashtags(tokens)
@@ -36,7 +36,7 @@ def normalize_hashtags(tokens):
         if t.tokentype == "hash":
             t.text = "#OCTOTHORPE"
 
-def normalize_ellipsis(tokens):
+def normalize_punct(tokens):
     for t in tokens:
         if t.tokentype == "punc":
             if t.text == ".." or t.text == "...":

### 2014-07-30 src/conductor.py
Templated the full table 1 and wrote a set of tests for the table in the makefile

@@ -34,13 +34,16 @@ def parse_args():
             help="This parameter changes the cutoff for training for max ent ")
     parser.add_argument("--numIterations", type=int,
             help="This parameter changes the cutoff for training for max ent ")
-    parser.add_argument("--validationMetric", default="none",
+    parser.add_argument("--validation_metric", default="none",
             help="This changes the metric for validation set evaluation")
 
     parser.add_argument("--no-uncommon-selection", dest="uncommon_selection",
             action="store_false", help="This toggles whither word selection is on off")
     parser.add_argument("--no-stopword-removal", dest="stopword_removal",
             action="store_false", help="This toggles whither stopword removal is on off")
+
+    parser.add_argument("--no-normalize", dest="no_normalize",
+            action="store_true", help="This toggles whither anything is normalized")
     parser.add_argument("--no-normalize-words", dest="normalize_words",
             action="store_false", help="This toggles whither words are normalized")
     parser.add_argument("--no-normalize-punct", dest="normalize_punct",
@@ -65,7 +68,7 @@ def parse_args():
         raise Exception("Classifier type must be one of: " + " ".join(classifier_types))
     if args.labels not in labels:
         raise Exception("Labels must be one of: " + " ".join(labels))
-    if args.validationMetric not in val_metrics:
+    if args.validation_metric not in val_metrics:
         raise Exception("Validation metrics must be one of: " + " ".join(val_metrics))
     return args
 
@@ -79,20 +82,21 @@ if __name__ == "__main__":
 
     print "Normalizing dataset..."
     #tokens = normalize.__call__(tokens) # Normalize the tokens
-    if args.normalize_words:
-        normalize.normalize_words(tokens)
-    if args.normalize_punct:
-        normalize.normalize_punct(tokens)
-    if args.normalize_emoticons:
-        normalize.normalize_emoticons(tokens)
-    if args.normalize_users:
-        normalize.normalize_users(tokens)
-    if args.normalize_hashtags:
-        normalize.normalize_hashtags(tokens)
-    if args.normalize_nums:
-        normalize.normalize_nums(tokens)
-    if args.normalize_urls:
-        normalize.normalize_urls(tokens)
+    if args.no_normalize:
+        if args.normalize_words:
+            normalize.normalize_words(tokens)
+        if args.normalize_punct:
+            normalize.normalize_punct(tokens)
+        if args.normalize_emoticons:
[…]

### 2014-07-30 paper/paper.tex
Templated the full table 1 and wrote a set of tests for the table in the makefile
Fixed some mistakes in the code and wrote a single make target to make one table col

@@
 supplemental data, respectively.
+
+The dataset for the task consists of 6225 labelled Tweets. 36.66\% of the
+corpus has `positive' label, 14.04\% has a `negative' label, 49.30\% has a
+label that conveys neutral sentiment. This neutral label is one of `neutral',
+`objective', or `objective-OR-neutral'.
 
@@
     \begin{center}
-    \begin{tabular}{|c|c|r|r|r|r|}
+    \begin{tabular}{|c|c|c|c|r|r|r|r|}
         \hline
-        Description & Stopwords & Run 1 & Run 2 & Run 3 & $\mu$ F\\
+        Description & Stopwords & Uncommon  & Normalize & Run 1 & Run 2 & Run 3 & $\mu F$\\
         \hline
-        MaxEnt      & Yes       & 0.0   & 0.0   & 0     & 0 \\
-        \dots       & No        & 0.0   & 0.0   & 0     & 0 \\
-        Naive Bayes & Yes       & 0.0   & 0.0   & 0     & 0 \\
-        \dots       & No        & 0.0   & 0.0   & 0     & 0 \\
+        MaxEnt      & Yes       & Yes       & Yes       & 50.97 & 0.0   & 0.0   & 0.0 \\
+        \dots       & Yes       & Yes       & No        & 56.21 & 0.0   & 0.0   & 0.0 \\
+        \dots       & Yes       & No        & Yes       & 51.25 & 0.0   & 0.0   & 0.0 \\
+        \dots       & Yes       & No        & No        & 54.44 & 0.0   & 0.0   & 0.0 \\
+        \dots       & No        & Yes       & Yes       & 50.71 & 0.0   & 0.0   & 0.0 \\
+        \dots       & No        & Yes       & No        & 51.03 & 0.0   & 0.0   & 0.0 \\
+        \dots       & No        & No        & Yes       & 50.41 & 0.0   & 0.0   & 0.0 \\
+        \dots       & No        & No        & No        & 51.56 & 0.0   & 0.0   & 0.0 \\
+        Naive Bayes & Yes       & Yes       & Yes       & 50.27 & 0.0   & 0.0   & 0.0 \\
+        \dots       & Yes       & Yes       & No        & 50.27 & 0.0   & 0.0   & 0.0 \\
+        \dots       & Yes       & No        & Yes       & 50.85 & 0.0   & 0.0   & 0.0 \\
+        \dots       & Yes       & No        & No        & 52.12 & 0.0   & 0.0   & 0.0 \\
+        \dots       & No        & Yes       & Yes       & 47.19 & 0.0   & 0.0   & 0.0 \\
+        \dots       & No        & Yes       & No        & 50.56 & 0.0   & 0.0   & 0.0 \\
+        \dots       & No        & No        & Yes       & 49.82 & 0.0   & 0.0   & 0.0 \\
+        \dots       & No        & No        & No        & 52.15 & 0.0   & 0.0   & 0.0 \\
         \hline
@@
 \end{table}
+
+%TODO write about the number of features
 

### 2014-07-30 src/conductor.py

@@ -42,8 +42,8 @@ def parse_args():
     parser.add_argument("--no-stopword-removal", dest="stopword_removal",
             action="store_false", help="This toggles whither stopword removal is on off")
 
-    parser.add_argument("--no-normalize", dest="no_normalize",
-            action="store_true", help="This toggles whither anything is normalized")
+    parser.add_argument("--no-normalize", dest="normalize",
+            action="store_false", help="This toggles whither anything is normalized")
     parser.add_argument("--no-normalize-words", dest="normalize_words",
             action="store_false", help="This toggles whither words are normalized")
     parser.add_argument("--no-normalize-punct", dest="normalize_punct",
@@ -82,32 +82,31 @@ if __name__ == "__main__":
 
     print "Normalizing dataset..."
     #tokens = normalize.__call__(tokens) # Normalize the tokens
-    if args.no_normalize:
-        if args.normalize_words:
-            normalize.normalize_words(tokens)
-        if args.normalize_punct:
-            normalize.normalize_punct(tokens)
-        if args.normalize_emoticons:
-            normalize.normalize_emoticons(tokens)
-        if args.normalize_users:
-            normalize.normalize_users(tokens)
-        if args.normalize_hashtags:
-            normalize.normalize_hashtags(tokens)
-        if args.normalize_nums:
-            normalize.normalize_nums(tokens)
-        if args.normalize_urls:
-            normalize.normalize_urls(tokens)
+    if args.normalize and args.normalize_words:
+        normalize.normalize_words(tokens)
+    if args.normalize and args.normalize_punct:
+        normalize.normalize_punct(tokens)
+    if args.normalize and args.normalize_emoticons:
+        normalize.normalize_emoticons(tokens)
+    if args.normalize and args.normalize_users:
+        normalize.normalize_users(tokens)
+    if args.normalize and args.normalize_hashtags:
+        normalize.normalize_hashtags(tokens)
+    if args.normalize and args.normalize_nums:
+        normalize.normalize_nums(tokens)
+    if args.normalize and args.normalize_urls:
+        normalize.normalize_urls(tokens)
 
     print "Transforming dataset..."
     feature_list = dictizer.__call__(tokens)
 
     if args.stopword_removal:
         print "Removing stopwords from the dataset..."
-        feature_list = wordselection.remove_uncommon(feature_list)
+        feature_list = wordselection.remove_stopwords(feature_list)
 
     if args.uncommon_selection:
[…]

### 2014-07-31 paper/paper.tex
Sent a draft to Fei Song. Hopefully this will go ok

--- 2014-07-30 paper/paper.tex
@@
     \begin{center}
-    \begin{tabular}{|c|c|r|r|r|r|}
+    \begin{tabular}{|c||c|c|c|c|r|r|r|r|}
         \hline
-        Description & Stopwords & Run 1 & Run 2 & Run 3 & $\mu$ F\\
+          & Classifier  & Stopwords & Uncommon  & Normalize & Run 1 & Run 2 & Run 3 & $\mu F$\\
                     \hline
-        MaxEnt      & Yes       & 0.0   & 0.0   & 0     & 0 \\
-        \dots       & No        & 0.0   & 0.0   & 0     & 0 \\
-        Naive Bayes & Yes       & 0.0   & 0.0   & 0     & 0 \\
-        \dots       & No        & 0.0   & 0.0   & 0     & 0 \\
+        a & MaxEnt      & Yes       & Yes       & Yes       & 51.55 & 52.80 & 54.09 & 52.81 \\
+        b & \dots       & Yes       & Yes       & No        & 51.10 & 49.34 & 50.23 & 50.22 \\
+        c & \dots       & Yes       & No        & Yes       & 53.51 & 51.97 & 52.06 & 52.51 \\
+        d & \dots       & Yes       & No        & No        & 54.55 & 48.77 & 49.51 & 50.94 \\
+        e & \dots       & No        & Yes       & Yes       & 50.88 & 50.55 & 52.09 & 51.17 \\
+        f & \dots       & No        & Yes       & No        & 52.46 & 50.64 & 54.11 & 52.40 \\
+        g & \dots       & No        & No        & Yes       & 49.80 & 56.26 & 54.13 & 53.40 \\
+        h & \dots       & No        & No        & No        & 50.59 & 50.91 & 50.67 & 50.72 \\
+        i & Naive Bayes & Yes       & Yes       & Yes       & 50.89 & 50.34 & 51.64 & 50.96 \\
+        j & \dots       & Yes       & Yes       & No        & 48.56 & 46.99 & 51.01 & 48.85 \\
+        k & \dots       & Yes       & No        & Yes       & 51.55 & 51.22 & 49.79 & 50.85 \\
+        l & \dots       & Yes       & No        & No        & 47.03 & 50.45 & 49.01 & 48.83 \\
+        m & \dots       & No        & Yes       & Yes       & 47.95 & 51.91 & 49.67 & 49.36 \\
+        n & \dots       & No        & Yes       & No        & 47.88 & 50.02 & 48.78 & 48.89 \\
+        o & \dots       & No        & No        & Yes       & 50.09 & 50.83 & 51.77 & 50.90 \\
+        p & \dots       & No        & No        & No        & 51.15 & 50.05 & 47.27 & 49.49 \\
         \hline
@@
     \end{center}
-    \caption{Results of variations on feature selection and training. Sorted by
-        average F-score.}
+    \caption{Results of variations on feature selection and training.}
     \label{table:results}
 \end{table}
+
+%TODO write about the number of features
 
@@
 
-I am great and without reproach.
+\textit{Note: I would like to finish the results section before I start this section }
 

### 2014-07-31 paper/paper.tex
Wrote a bunch more.

--- 2014-07-30 paper/paper.tex
@@
 
-Draft 2 %TODO ditch this
+Draft 3 %TODO ditch this
 
@@
 \newpage
-%\pagestyle{headings}
 \setcounter{page}{1}
@@
 
-TODO establish baseline here
+The proceedings of SemEval-2013 establishes the `Majority Baseline' for the
+task to be an F-score of 29.19. How this number is calculated is not discusses
+in paper.
+
+The baseline for this project is established by running the Maximum Entropy
+classifier without any Stop word removal, Uncommon word removal, Or feature
+Normalization. The F-score that is achieved is 50.72. See Experiment \textit{g}
+in Table \ref{table:results} to see the results in context.
 
@@
     \begin{center}
-    \begin{tabular}{|c|c|r|r|r|r|}
+    \begin{tabular}{|c||c|c|c|c|r|r|r|r|}
         \hline
-        Description & Stopwords & Run 1 & Run 2 & Run 3 & $\mu$ F\\
+                   & Classifier  & Stopwords & Uncommon  & Normalize & Run 1 & Run 2 & Run 3 & $\mu F$\\
         \hline
-        MaxEnt      & Yes       & 0.0   & 0.0   & 0     & 0 \\
-        \dots       & No        & 0.0   & 0.0   & 0     & 0 \\
-        Naive Bayes & Yes       & 0.0   & 0.0   & 0     & 0 \\
-        \dots       & No        & 0.0   & 0.0   & 0     & 0 \\
+        \textit{a} & MaxEnt      & Yes       & Yes       & Yes       & 51.55 & 52.80 & 54.09 & 52.81 \\
+        \textit{b} & \dots       & Yes       & Yes       & No        & 51.10 & 49.34 & 50.23 & 50.22 \\
+        \textit{c} & \dots       & Yes       & No        & Yes       & 53.51 & 51.97 & 52.06 & 52.51 \\
+        \textit{d} & \dots       & Yes       & No        & No        & 54.55 & 48.77 & 49.51 & 50.94 \\
+        \textit{e} & \dots       & No        & Yes       & Yes       & 50.88 & 50.55 & 52.09 & 51.17 \\
+        \textit{f} & \dots       & No        & Yes       & No        & 52.46 & 50.64 & 54.11 & 52.40 \\
+        \textit{g} & \dots       & No        & No        & Yes       & 49.80 & 56.26 & 54.13 & 53.40 \\
+        \textit{h} & \dots       & No        & No        & No        & 50.59 & 50.91 & 50.67 & 50.72 \\
+        \textit{i} & Naive Bayes & Yes       & Yes       & Yes       & 50.89 & 50.34 & 51.64 & 50.96 \\
+        \textit{j} & \dots       & Yes       & Yes       & No        & 48.56 & 46.99 & 51.01 & 48.85 \\
+        \textit{k} & \dots       & Yes       & No        & Yes       & 51.55 & 51.22 & 49.79 & 50.85 \\
+        \textit{l} & \dots       & Yes       & No        & No        & 47.03 & 50.45 & 49.01 & 48.83 \\
+        \textit{m} & \dots       & No        & Yes       & Yes       & 47.95 & 51.91 & 49.67 & 49.36 \\
+        \textit{n} & \dots       & No        & Yes       & No        & 47.88 & 50.02 & 48.78 & 48.89 \\
+        \textit{o} & \dots       & No        & No        & Yes       & 50.09 & 50.83 & 51.77 & 50.90 \\
+        \textit{p} & \dots       & No        & No        & No        & 51.15 & 50.05 & 47.27 & 49.49 \\
         \hline
@@
     \end{center}
-    \caption{Results of variations on feature selection and training. Sorted by
-        average F-score.}
+    \caption{Results of variations on feature selection and training. The
+    `Citation' column indicates what type of classifier is being used. The
+    `Stopwords' column indicates if stop words have been removed. The `Uncommon'
+    column indicates if words with a document frequency lower than the threshold
+    (in this case more than one occurrence) have been removed. The `Normalize'
+    column indicates if the any steps have been taken to normalize features.}
     \label{table:results}
 \end{table}
+
+The results in Table \ref{table:results} indicates that there is not lot of
+difference variation between experiments. The best average F-score is
+experiment \textit{g}, however $\sigma_{g} = 2.69$. In contrast, the second
+best F-score is experiment \textit{a} exhibits more consistent classification
+with $\sigma_{a} = 1.04$.
+
+%TODO write about the number of features
 
@@
         Oasis      & 53.84 \\
-        \textbf{Best MaxEnt}& \textbf{53.32} \\
         NTNU       & 53.23 \\
+        \textbf{Best MaxEnt}& \textbf{52.81} \\
         UoM        & 51.81 \\
+        \textbf{Best Navie Bayes}& \textbf{50.96} \\
         SSA-UO     & 50.17 \\
@@
         9 more teams &  \textless\ 50 \\
-        $\ldots$   & $\ldots$ \\
         \hline

### 2014-07-31 paper/paper.tex
Added a section about the number of features

@@
 
-%TODO write about the number of features
+Number of features retained varies from Tweet to Tweet. To summarize the number
+of features retained after different process Table \ref{table:numfeatures}
+presents the mean number of features per Tweet for positive, neutral, negative
+examples as well as an overall average.
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{|c||r|r|r|r|}
+        \hline
+                               & Positive & Neutral & Negative & Overall \\
+        \hline
+        \textit{a}, \textit{i} & 14.85    & 14.06   & 15.10    & 14.49 \\
+        \textit{b}, \textit{j} & 14.91    & 14.30   & 15.30    & 14.67 \\
+        \textit{c}, \textit{k} & 15.95    & 15.40   & 16.33    & 15.73 \\
+        \textit{d}, \textit{l} & 17.13    & 16.86   & 17.41    & 17.04 \\
+        \textit{e}, \textit{m} & 18.54    & 17.81   & 18.82    & 18.22 \\
+        \textit{f}, \textit{n} & 18.43    & 17.87   & 18.85    & 18.21 \\
+        \textit{g}, \textit{o} & 19.64    & 19.15   & 20.05    & 19.46 \\
+        \textit{h}, \textit{p} & 20.65    & 20.45   & 20.96    & 20.58 \\
+        \hline
+    \end{tabular}
+    \end{center}
+    \caption{The average number of features in each experiment}
+    \label{table:numfeatures}
+\end{table}
+
+As presented in Table \ref{table:numfeatures}, the number of features decreases
+each time a feature set simplification method is turned on. Normalization does
+not appear to significantly reduce the number of features per Tweet. This make
+sense because the number of features in would only be reduced if it contained
+tokens that were different before simplification and were the same after (e.g.
+A Tweet that contained `2' and `3' before normalization would only contain the
+feature `\#NUM' after normalization).
 

### 2014-07-31 src/conductor.py
Got the program to spit out the number of features regardless if word selection is on. Added a colum to the table

@@ -36,6 +36,8 @@ def parse_args():
             help="This parameter changes the cutoff for training for max ent ")
     parser.add_argument("--validation_metric", default="none",
             help="This changes the metric for validation set evaluation")
+    parser.add_argument("--df_cutoff", type=int, default=1,
+            help="This parameter changes the document frequency cutoff")
 
     parser.add_argument("--no-uncommon-selection", dest="uncommon_selection",
             action="store_false", help="This toggles whither word selection is on off")
@@ -100,13 +102,17 @@ if __name__ == "__main__":
     print "Transforming dataset..."
     feature_list = dictizer.__call__(tokens)
 
+    docfreq = wordselection.calculate_docfreq(feature_list)
+
     if args.stopword_removal:
         print "Removing stopwords from the dataset..."
         feature_list = wordselection.remove_stopwords(feature_list)
 
     if args.uncommon_selection:
         print "Removing uncommon words from the dataset..."
-        feature_list = wordselection.remove_uncommon(feature_list)
+        feature_list = wordselection.remove_uncommon(feature_list, docfreq, args.df_cutoff)
+
+    wordselection.print_reatined_features(docfreq, args.df_cutoff)
 
     # Write the features out to a file
     with open("filtered_docs.txt", "w") as w:

### 2014-07-31 src/wordselection.py

@@ -31,10 +31,8 @@ def remove_stopwords(input_list):
         output_list.append([stopword_free_dict, pair[1]])
     return output_list
 
-def remove_uncommon(input_list, count=1):
-    output_list = []
+def calculate_docfreq(input_list):
     word_docfreq = {}
-
     # Count document frequency for each word
     for pair in input_list:
         for k in pair[0].keys():
@@ -47,21 +45,24 @@ def remove_uncommon(input_list, count=1):
     with open("features.txt", "w") as w:
         for feature in sorted(word_docfreq, key=word_docfreq.get, reverse=True):
             w.write(feature + "\t" + str(word_docfreq[feature]) + "\n")
+    return word_docfreq
 
+def print_reatined_features(word_docfreq, df_cutoff):
     # Count number of features
     num_features = 0
     for word in word_docfreq:
-        if word_docfreq[word] > count:
+        if word_docfreq[word] > df_cutoff:
             num_features += 1
     print "Total retained features:", num_features
 
+def remove_uncommon(input_list, word_docfreq, df_cutoff):
+    output_list = []
     # Keep only the common words
     for pair in input_list:
         uncommon_free_dict = {}
         for k in pair[0].keys():
-            if word_docfreq[k] > count:
+            if word_docfreq[k] > df_cutoff:
                 uncommon_free_dict[k] = pair[0][k]
         output_list.append([uncommon_free_dict, pair[1]])
-
     return output_list
 

### 2014-08-01 paper/paper.tex
Got the program to spit out the number of features regardless if word selection is on. Added a colum to the table
Moved the argument outside. Ditched non-relevant data

@@
 
-Utilizing Maximum Entropy Classification for Sentiment Analysis in Twitter
-Messages
+Utilizing Maximum Entropy Classification for Sentiment Analysis in Twitter Messages
 
@@
     \begin{center}
-    \begin{tabular}{|c||r|r|r|r|}
+    \begin{tabular}{|c||r|r|r|r|r|}
         \hline
-                               & Positive & Neutral & Negative & Overall \\
+                               & Positive & Neutral & Negative & Overall & Total \\
         \hline
-        \textit{a}, \textit{i} & 14.85    & 14.06   & 15.10    & 14.49 \\
-        \textit{b}, \textit{j} & 14.91    & 14.30   & 15.30    & 14.67 \\
-        \textit{c}, \textit{k} & 15.95    & 15.40   & 16.33    & 15.73 \\
-        \textit{d}, \textit{l} & 17.13    & 16.86   & 17.41    & 17.04 \\
-        \textit{e}, \textit{m} & 18.54    & 17.81   & 18.82    & 18.22 \\
-        \textit{f}, \textit{n} & 18.43    & 17.87   & 18.85    & 18.21 \\
-        \textit{g}, \textit{o} & 19.64    & 19.15   & 20.05    & 19.46 \\
-        \textit{h}, \textit{p} & 20.65    & 20.45   & 20.96    & 20.58 \\
+        \textit{a}, \textit{i} & 14.85    & 14.06   & 15.10    & 14.49   & 5964 \\
+        \textit{b}, \textit{j} & 14.91    & 14.30   & 15.30    & 14.67   & 7493 \\
+        \textit{c}, \textit{k} & 15.95    & 15.40   & 16.33    & 15.73   & 0 \\
+        \textit{d}, \textit{l} & 17.13    & 16.86   & 17.41    & 17.04   & 0 \\
+        \textit{e}, \textit{m} & 18.54    & 17.81   & 18.82    & 18.22   & 5993 \\
+        \textit{f}, \textit{n} & 18.43    & 17.87   & 18.85    & 18.21   & 7522 \\
+        \textit{g}, \textit{o} & 19.64    & 19.15   & 20.05    & 19.46   & 0 \\
+        \textit{h}, \textit{p} & 20.65    & 20.45   & 20.96    & 20.58   & 0 \\
         \hline
@@
     \end{center}
-    \caption{The average number of features in each experiment}
+    \caption{`Positive', `Neutral', `Negative', and `Overall' refer to the
+    average number of features per Tweet in each experiment. `Total' refers to
+    the total number of different features in the dataset}
     \label{table:numfeatures}
 \end{table}
+
+% TODO finish table
 
@@
 feature `\#NUM' after normalization).
+
+\subsection{Most Informative Features}
+
+\begin{verbatim}
+  -3.176 excited==True and label is 'neutral'
+   2.328 lied==True and label is 'negative'
+   2.279 availability==True and label is 'negative'
+  -2.258 excited==True and label is 'negative'
+  -2.180 EM_HAPPY==True and label is 'negative'
+  -2.171 happy==True and label is 'neutral'
+  -2.098 birthday==True and label is 'negative'
+   2.016 shitty==True and label is 'negative'
+  -1.836 8th==True and label is 'positive'
+  -1.801 international==True and label is 'positive'
+   1.789 embarrassing==True and label is 'negative'
+  -1.762 went==True and label is 'negative'
+   1.702 releases==True and label is 'negative'
+  -1.672 love==True and label is 'negative'
+   1.650 lack==True and label is 'negative'
+   1.650 oneil==True and label is 'neutral'
+  -1.638 fun==True and label is 'neutral'
+   1.599 replay==True and label is 'negative'
+  -1.585 great==True and label is 'neutral'
+   1.577 asses==True and label is 'positive'
+   1.570 garlic==True and label is 'negative'
+  -1.564 pass==True and label is 'negative'
+   1.560 den==True and label is 'negative'
+   1.560 accepting==True and label is 'negative'
+  -1.557 sure==True and label is 'negative'
+   1.551 insensitive==True and label is 'negative'
+   1.547 calvin==True and label is 'negative'
+   1.532 jailed==True and label is 'negative'
+   1.520 lookin==True and label is 'neutral'
+   1.515 2c==True and label is 'negative'
+\end{verbatim}
 

### 2014-08-01 src/conductor.py

@@ -2,11 +2,9 @@
 
 # File       : conductor.py
 # Author     : Douglas Anderson
-# Description: Driver for my parser implementation
+# Description: Driver for sentiment anaysis implementation
 
 import os, sys
-import argparse
-import math
 
 import tokenize
 import normalize
@@ -16,63 +14,11 @@ import wordselection
 import dictizer
 import split_dataset
 from Token import Token
+from parse_args import parse_args
 from train import maxent_classifier
 from train import maxent_classifier_with_validation
 from train import naive_bayes_classifier
 
-def parse_args():
-    classifier_types = ["max_ent", "bayes"]
-    labels = ["pn", "pnn"]
-    val_metrics = ["none", "accuracy", "fscore"]
-    parser = argparse.ArgumentParser(description="Scan a tweet to determine it's tokens")
-    parser.add_argument("--file", type=str,
-            help="The file name containing the text to be scanned")
-    parser.add_argument("items", type=int, help="The number of items to use")
-    parser.add_argument("--minlldelta", type=float,
-            help="This parameter changes the cutoff of training for max ent ")
-    parser.add_argument("--minll", type=float,
-            help="This parameter changes the cutoff for training for max ent ")
-    parser.add_argument("--numIterations", type=int,
-            help="This parameter changes the cutoff for training for max ent ")
-    parser.add_argument("--validation_metric", default="none",
-            help="This changes the metric for validation set evaluation")
-    parser.add_argument("--df_cutoff", type=int, default=1,
-            help="This parameter changes the document frequency cutoff")
-
-    parser.add_argument("--no-uncommon-selection", dest="uncommon_selection",
-            action="store_false", help="This toggles whither word selection is on off")
-    parser.add_argument("--no-stopword-removal", dest="stopword_removal",
-            action="store_false", help="This toggles whither stopword removal is on off")
-
-    parser.add_argument("--no-normalize", dest="normalize",
-            action="store_false", help="This toggles whither anything is normalized")
-    parser.add_argument("--no-normalize-words", dest="normalize_words",
-            action="store_false", help="This toggles whither words are normalized")
-    parser.add_argument("--no-normalize-punct", dest="normalize_punct",
-            action="store_false", help="This toggles whither words are normalized")
-    parser.add_argument("--no-normalize-emoticons", dest="normalize_emoticons",
-            action="store_false", help="This toggles whither words are normalized")
[…]

### 2014-08-01 src/conductor.py
On my way to a program with cross validation

@@ -2,7 +2,7 @@
 
 # File       : conductor.py
 # Author     : Douglas Anderson
-# Description: Driver for sentiment anaysis implementation
+# Description: Simple driver for sentiment analysis implementation
 
 import os, sys
 

### 2014-08-01 src/parse_args.py

@@ -1,0 +1,67 @@
+#!/usr/bin/env python
+
+# File       : parse_args.py
+# Author     : Douglas Anderson
+# Description: Command line options for argument parseing
+
+import argparse
+
+def parse_args():
+    classifier_types = ["max_ent", "bayes"]
+    valid_fold_numbers = [5, 10]
+    labels = ["pn", "pnn"]
+    val_metrics = ["none", "accuracy", "fscore"]
+    parser = argparse.ArgumentParser(description="Scan a tweet to determine it's tokens")
+    parser.add_argument("--file", type=str,
+            help="The file name containing the text to be scanned")
+    parser.add_argument("items", type=int, help="The number of items to use")
+    parser.add_argument("--minlldelta", type=float,
+            help="This parameter changes the cutoff of training for max ent ")
+    parser.add_argument("--minll", type=float,
+            help="This parameter changes the cutoff for training for max ent ")
+    parser.add_argument("--numIterations", type=int,
+            help="This parameter changes the cutoff for training for max ent ")
+    parser.add_argument("--validation_metric", default="none",
+            help="This changes the metric for validation set evaluation")
+    parser.add_argument("--df-cutoff", type=int, default=1,
+            help="This parameter changes the document frequency cutoff")
+    parser.add_argument("--num-folds", type=int, default=5,
+            help="This parameter changes number of folds for cross-validation")
+
+    parser.add_argument("--no-uncommon-selection", dest="uncommon_selection",
+            action="store_false", help="This toggles whither word selection is on off")
+    parser.add_argument("--no-stopword-removal", dest="stopword_removal",
+            action="store_false", help="This toggles whither stopword removal is on off")
+
+    parser.add_argument("--no-normalize", dest="normalize",
+            action="store_false", help="This toggles whither anything is normalized")
+    parser.add_argument("--no-normalize-words", dest="normalize_words",
+            action="store_false", help="This toggles whither words are normalized")
+    parser.add_argument("--no-normalize-punct", dest="normalize_punct",
+            action="store_false", help="This toggles whither words are normalized")
+    parser.add_argument("--no-normalize-emoticons", dest="normalize_emoticons",
+            action="store_false", help="This toggles whither words are normalized")
+    parser.add_argument("--no-normalize-users", dest="normalize_users",
+            action="store_false", help="This toggles whither users are normalized")
+    parser.add_argument("--no-normalize-hashtags", dest="normalize_hashtags",
[…]

### 2014-08-01 src/split_dataset.py

@@ -23,3 +23,10 @@ def __call__(feature_list, test_size, validation_size=0.0):
     train_set = feature_list
     return train_set, validation_set, test_set
 
+def partition(flist, n):
+    outlist = []
+    splitsize = int(math.ceil(len(flist)/float(n)))
+    for i in range(0, len(flist), splitsize):
+        outlist.append(flist[i:i+splitsize])
+    return outlist
+

### 2014-08-01 src/statsify.py

@@ -56,7 +56,7 @@ def print_bi_confusion_matrix(cm):
     print "neg\t",cm["negative"]["positive"],"\t",cm["negative"]["negative"]
 
 
-def calculate_fscore(classifier, test_set, trace=True):
+def calculate_metrics(classifier, test_set, trace=True):
     cm = {
             "positive": {"positive": 0, "neutral": 0, "negative": 0},
             "neutral":  {"positive": 0, "neutral": 0, "negative": 0},
@@ -126,5 +126,12 @@ def calculate_fscore(classifier, test_set, trace=True):
         print "F pos   :\t", stats["Fpos"]
         print "F neg   :\t", stats["Fneg"]
         print "Fscore  :\t", stats["F"]
-    return stats["F"]
+    #return stats["F"]
+    return stats
+
+def calculate_fscore(classifier, test_set):
+    x = calculate_metrics(classifier, test_set, trace=False)["F"]
+    print "x:", x
+    return x
+
 

### 2014-08-01 src/train.py

@@ -11,7 +11,7 @@ class classifier:
         pass
 
     def test(self, test_set, labels):
-        statsify.calculate_fscore(self.classifier, test_set, trace=True)
+        return statsify.calculate_metrics(self.classifier, test_set)
 
     def show_informitive_features(self, numFeatures):
         self.classifier.show_most_informative_features(numFeatures)
@@ -49,7 +49,7 @@ class maxent_classifier_with_validation(classifier):
         if metric_type == "accuracy":
             metric = nltk.classify.accuracy(self.classifier, validation_set)
         else:
-            metric = statsify.calculate_fscore(self.classifier, validation_set, trace=False)
+            metric = statsify.calculate_fscore(self.classifier, validation_set)
         best_iteration = 0
         best_metric = metric
         best_weights = self.classifier.weights()
@@ -62,7 +62,7 @@ class maxent_classifier_with_validation(classifier):
             if metric_type == "accuracy":
                 metric = nltk.classify.accuracy(self.classifier, validation_set)
             else:
-                metric = statsify.calculate_fscore(self.classifier, validation_set, trace=False)
+                metric = statsify.calculate_fscore(self.classifier, validation_set)
             print "Iteration {} {}  :\t{}".format(iter_count, metric_type, metric)
             print "{} delta  :\t{}".format(metric_type, metric - best_metric)
             if(metric - best_metric) <= 0.0:

### 2014-08-01 src/crossval.py
Removed the old dataset. Somehow my results are a lot better

@@ -1,10 +1,12 @@
 #!/usr/bin/env python
 
-# File       : conductor.py
+# File       : crossval.py
 # Author     : Douglas Anderson
-# Description: Simple driver for sentiment analysis implementation
+# Description: Cross validation driver for sentiment analysis implementation
 
 import os, sys
+import numpy
+from itertools import permutations
 
 import tokenize
 import normalize
@@ -20,8 +22,7 @@ from train import maxent_classifier_with_validation
 from train import naive_bayes_classifier
 
 
-if __name__ == "__main__":
-    args = parse_args()
+def main(args):
     print "Opening dataset..."
     tokens = tokenize.open_tweets_file("../data/b.tsv", 0, args.items)
 
@@ -69,30 +70,64 @@ if __name__ == "__main__":
     statsify.__call__(feature_list, args.labels)
 
     print "Splitting the dataset..."
-    if args.validation_metric == "none":
-        train_set, _, test_set = split_dataset.__call__(feature_list, 0.2)
-    else:
-        train_set, validation_set, test_set = split_dataset.__call__(feature_list, 0.2, validation_size=0.2)
+    partitions = split_dataset.partition(feature_list, args.num_folds)
 
-    if args.classifier_type == "max_ent":
-        if args.minlldelta:
-            classifier = maxent_classifier(train_set, lldelta=args.minlldelta)
-        elif args.minll:
-            classifier = maxent_classifier(train_set, ll=args.minll)
-        elif args.validation_metric != "none":
-            classifier = maxent_classifier_with_validation(train_set, validation_set,
+    print len(partitions), "Partitions"
+
+    accumulation_dict = {}
+
+    for i, fold in enumerate(generate_folds(partitions)):
+        print "Fold number:", i, "Looks like:", "".join(fold)
+        #print fold
+        print "\nTraining"
+        train_set = select_set("t", fold, partitions)
+        validation_set = select_set("v", fold, partitions)
+        test_set = select_set("T", fold, partitions)
+        classifier = maxent_classifier_with_validation(train_set, validation_set,
                     args.validation_metric, 3)
-        elif args.numIterations:
-            classifier = maxent_classifier(train_set, iterations=args.numIterations)
-        else:
-            print "Error no cut off set"
-            sys.exit(0)
-    else:
-        classifier = naive_bayes_classifier(train_set)
+        print "\nTesting...",
+        results_dict = classifier.test(test_set, args.labels, trace=False)
[…]

### 2014-08-01 src/statsify.py

@@ -130,8 +130,8 @@ def calculate_metrics(classifier, test_set, trace=True):
     return stats
 
 def calculate_fscore(classifier, test_set):
-    x = calculate_metrics(classifier, test_set, trace=False)["F"]
-    print "x:", x
-    return x
+    return calculate_metrics(classifier, test_set, trace=False)["F"]
 
+def accumulate_fscore(classifier, test_set):
+    pass
 

### 2014-08-01 src/train.py

@@ -10,10 +10,10 @@ class classifier:
     def __init__(self, train_set):
         pass
 
-    def test(self, test_set, labels):
-        return statsify.calculate_metrics(self.classifier, test_set)
+    def test(self, test_set, labels, trace=True):
+        return statsify.calculate_metrics(self.classifier, test_set, trace=trace)
 
-    def show_informitive_features(self, numFeatures):
+    def show_informative_features(self, numFeatures):
         self.classifier.show_most_informative_features(numFeatures)
 
     def inspect_errors(self, test_set):

### 2014-08-01 src/crossval.py
Formmated the training process so that training is indented

@@ -72,20 +72,25 @@ def main(args):
     print "Splitting the dataset..."
     partitions = split_dataset.partition(feature_list, args.num_folds)
 
-    print len(partitions), "Partitions"
+    #print len(partitions), "Partitions"
+    #for p in partitions:
+        #print
+        #for t in p:
+            #print t
+    #return
 
     accumulation_dict = {}
 
     for i, fold in enumerate(generate_folds(partitions)):
-        print "Fold number:", i, "Looks like:", "".join(fold)
+        print "Fold number: {} looks like: {}".format(i, "".join(fold))
         #print fold
-        print "\nTraining"
+        print "Training fold", i
         train_set = select_set("t", fold, partitions)
         validation_set = select_set("v", fold, partitions)
         test_set = select_set("T", fold, partitions)
         classifier = maxent_classifier_with_validation(train_set, validation_set,
                     args.validation_metric, 3)
-        print "\nTesting...",
+        print "Testing fold {}...".format(i),
         results_dict = classifier.test(test_set, args.labels, trace=False)
         #Add results to the accumulation dict
         for key in results_dict.keys():
@@ -93,7 +98,7 @@ def main(args):
              accumulation_dict[key].append(results_dict[key])
          except KeyError:
              accumulation_dict[key] = [results_dict[key]]
-        print "done."
+        print "done.\n"
         #classifier.show_informative_features(30)
         #classifier.inspect_errors(test_set)
 

### 2014-08-01 src/statsify.py

@@ -126,7 +126,6 @@ def calculate_metrics(classifier, test_set, trace=True):
         print "F pos   :\t", stats["Fpos"]
         print "F neg   :\t", stats["Fneg"]
         print "Fscore  :\t", stats["F"]
-    #return stats["F"]
     return stats
 
 def calculate_fscore(classifier, test_set):

### 2014-08-01 src/train.py

@@ -53,7 +53,7 @@ class maxent_classifier_with_validation(classifier):
         best_iteration = 0
         best_metric = metric
         best_weights = self.classifier.weights()
-        print "Iteration {} {}  :\t{}".format(iter_count, metric_type, metric)
+        print "  Iteration {} {}  :\t{}".format(iter_count, metric_type, metric)
         #while (metric - prev_metric) >= 0.0:
         while rounds_without_improvment < smoothing:
             iter_count += 1
@@ -63,8 +63,8 @@ class maxent_classifier_with_validation(classifier):
                 metric = nltk.classify.accuracy(self.classifier, validation_set)
             else:
                 metric = statsify.calculate_fscore(self.classifier, validation_set)
-            print "Iteration {} {}  :\t{}".format(iter_count, metric_type, metric)
-            print "{} delta  :\t{}".format(metric_type, metric - best_metric)
+            print "  Iteration {} {}  :\t{}".format(iter_count, metric_type, metric)
+            print "  {} delta  :\t{}".format(metric_type, metric - best_metric)
             if(metric - best_metric) <= 0.0:
                 rounds_without_improvment += 1
             else:
@@ -73,7 +73,7 @@ class maxent_classifier_with_validation(classifier):
                 best_metric = metric
                 best_weights = self.classifier.weights()
 
-        print "Restoring iteration {} weights".format(best_iteration)
+        print "  Restoring iteration {} weights".format(best_iteration)
         self.classifier.set_weights(best_weights)
 
 

### 2014-08-02 paper/figures/boxplot.R
Worked on a box plot for a while. Finally got it working

@@ -1,0 +1,21 @@
+
+library(ggplot2)
+
+#data <- read.table("box.csv", header=TRUE, col.names=c("y"))
+#data <- read.table("box.csv", col.names=c("X", "F"))
+data <- read.csv("boxplot.csv", header=TRUE)
+
+print(data)
+
+chart_title <- "Classifier Performance"
+xlab <- "Experiment"
+ylab <- "F-score"
+
+p <- ggplot(data, aes(x=factor(Label), y=F)) + geom_boxplot()
+p = p + scale_x_discrete("Labels", labels=c("A", "B"))
+p = p + ylim(c(0.25,0.75))
+p = p + ggtitle(chart_title)
+p = p + xlab(xlab)
+p = p + ylab(ylab)
+p = p + theme_minimal()
+p # Draw that sucker

### 2014-08-02 src/crossval.py

@@ -109,7 +109,6 @@ def main(args):
         print "{}-std:\t".format(key), numpy.std(accumulation_dict[key])
 
 
-
 def select_set(set_type, fold, partitions):
     output_set = []
     for i,x in enumerate(fold):
@@ -136,3 +135,4 @@ def generate_folds(partitions):
 if __name__ == "__main__":
     args = parse_args()
     main(args)
+

### 2014-08-02 paper/figures/boxplot.R
Changed the formatting of the doc but I am yet to number the sections

@@ -7,15 +7,14 @@ data <- read.csv("boxplot.csv", header=TRUE)
 
 print(data)
 
-chart_title <- "Classifier Performance"
+chart_title <- "Maximum Entropy Classifier Performance"
 xlab <- "Experiment"
 ylab <- "F-score"
+groups <- c("All", "Just Stopwords", "Just Uncommon", "Just Normalization", "Baseline")
 
 p <- ggplot(data, aes(x=factor(Label), y=F)) + geom_boxplot()
-p = p + scale_x_discrete("Labels", labels=c("A", "B"))
-p = p + ylim(c(0.25,0.75))
+p = p + scale_x_discrete(xlab, labels=groups)
+p = p + scale_y_continuous(ylab, limits=c(0.30, 0.60))
 p = p + ggtitle(chart_title)
-p = p + xlab(xlab)
-p = p + ylab(ylab)
 p = p + theme_minimal()
 p # Draw that sucker

### 2014-08-02 paper/figures/boxplot.R
Numbered sections. Hopefully fixed the crossfolds in the makefile

@@ -14,7 +14,11 @@ groups <- c("All", "Just Stopwords", "Just Uncommon", "Just Normalization", "Bas
 
 p <- ggplot(data, aes(x=factor(Label), y=F)) + geom_boxplot()
 p = p + scale_x_discrete(xlab, labels=groups)
-p = p + scale_y_continuous(ylab, limits=c(0.30, 0.60))
+p = p + scale_y_continuous(ylab, limits=c(0.35, 0.55))
 p = p + ggtitle(chart_title)
 p = p + theme_minimal()
+
+#png("boxplot.png")
 p # Draw that sucker
+#dev.off()
+ggsave("boxplot.png")

### 2014-08-02 paper/paper.tex
On my way to a program with cross validation
Changed the formatting of the doc but I am yet to number the sections
Numbered sections. Hopefully fixed the crossfolds in the makefile
Added a license. Stubbed the changed Fei Song recomended. Fixed the data for the boxplot

@@
-\documentclass[12pt]{article}
+%\documentclass[12pt]{article}
+\documentclass[final,3p,12pt]{elsarticle}
 \usepackage{enumerate}
@@
 \usepackage{graphicx}
-\usepackage[margin=1.0in]{geometry}
+%\usepackage[margin=1.0in]{geometry}
 \usepackage{float}
@@
 \restylefloat{table}
-
-\makeatletter
-\renewcommand\@seccntformat[1]{}
-\makeatother
 
@@
 
-\subsection{Topic Area}
-
 Sentiment analysis is simply a classification task that attempts to label
@@
 
-The dataset for the task consists of 6225 labelled Tweets. 36.66\% of the
-corpus has `positive' label, 14.04\% has a `negative' label, 49.30\% has a
-label that conveys neutral sentiment. This neutral label is one of `neutral',
-`objective', or `objective-OR-neutral'.
-
 \section{Background}
@@
 
+%TODO Sentiment Analysis
+%TODO Text Classification
+%TODO Feature Selection
+
 \textit{Note: This section needs to be expanded. I am just not sure what else to write about...}
 
-%TODO extend
-
-\section{Approach}
+\section{Our Implementation}
 
@@
 
-\subsection{Implementation}
+% TODO expand on IIS
+
+\subsection{Preprocessing and Feature Selection}
 
@@
 
+    %TODO talk about cross validation
+
 \end{enumerate}
 
-\subsection{Avoiding overfitting}
+\subsection{Training Optimization}
 
@@
 
-\section{Discussion}
+\section{Experiments and Discussion}
 
-\subsection{Evaluation Method}
+\subsection{Dataset}
+
+The dataset for the task consists of 6225 labelled Tweets. 36.66\% of the
+corpus has `positive' label, 14.04\% has a `negative' label, 49.30\% has a
+label that conveys neutral sentiment. This neutral label is one of `neutral',
+`objective', or `objective-OR-neutral'.
+
+\subsection{Evaluation Measures}
 
@@
 proceedings and the results of the task \cite{Nakov2013}. The paper establishes
-baseline in terms of $F$. $F$ can be calculated $F = (F_{pos} + F_{neg}) / 2$
-where $F_{pos} = 2 \frac{P_{pos}R_{pos}}{P_{pos} + R_{pos}}$ and $F_{neg}$ is
-calculated in a similar fashion. The \textit{Precision} measure for the
-positive label is $P_{pos} = \frac{\mathrm{\# of\ true\ postive}}{\mathrm{\#
-of\ true\ postive} + \mathrm{\# of\ false\ postive} }$. The \textit{Recall}
-measure for the positive label is defined as $R_{pos} = \frac{\mathrm{\# of\
-true\ postive}}{\mathrm{\# of\ true\ postive} + \mathrm{\# of\ false\ negative}
-}$
+baseline in terms of $F$. $F$ can be calculated as:
+\begin{equation}
+    F = \frac{2 \frac{P_{pos}R_{pos}}{P_{pos} + R_{pos}} +
+    2 \frac{P_{neg}R_{neg}}{P_{neg} + R_{neg}}}{2}
+\end{equation}
+
+Which can be simplified to:
+
+\begin{equation}
+    F = \frac{P_{pos}R_{pos}}{P_{pos} + R_{pos}} + \frac{P_{neg}R_{neg}}{P_{neg} + R_{neg}}
+\end{equation}
+
+The \textit{Precision} measure for the positive label is $P_{pos} =
+\frac{\mathrm{\# of\ true\ postive}}{\mathrm{\# of\ true\ postive} + \mathrm{\#
+of\ false\ postive} }$. The \textit{Recall} measure for the positive label is
+defined as $R_{pos} = \frac{\mathrm{\# of\ true\ postive}}{\mathrm{\# of\ true\
+postive} + \mathrm{\# of\ false\ negative} }$. $P_{neg}$ and $R_{neg}$ can be
+calculated in a similar fashion.
 
 \subsection{Baseline}
-
-The proceedings of SemEval-2013 establishes the `Majority Baseline' for the
-task to be an F-score of 29.19. How this number is calculated is not discusses
-in paper.
 
@@
 
-\subsection{Results}
+\subsection{Experimental Results}
 
@@
 
+% TODO Student T-test
+
 As presented in Table \ref{table:numfeatures}, the number of features decreases
@@
 \subsection{Most Informative Features}
+
+%TODO talk about the features
 
@@
 
-\subsection{Comparison to Workshop Participants}
+\subsection{Comparison to Other Systems}
 
@@
 
-\section{Conclusion}
+\section{Conclusions and Future Work}
+
+\subsection{Conclusions}
 
@@
 
-\section{Future Work}
+\subsection{Future Work}
 
-\subsection{Hashtags}
+\subsubsection{Hashtags}
 
@@
 
-\subsection{Users}
+\subsubsection{Users}
 
@@
 
-% Bibliography
+\section{References}
+
 \nocite{*}
@@
 
+\section{Appendices}
+
+\subsection{Implementation Source Code}
+
 \end{document}

### 2014-08-02 paper/figures/boxplot.R

@@ -12,13 +12,15 @@ xlab <- "Experiment"
 ylab <- "F-score"
 groups <- c("All", "Just Stopwords", "Just Uncommon", "Just Normalization", "Baseline")
 
-p <- ggplot(data, aes(x=factor(Label), y=F)) + geom_boxplot()
+cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+palette <- c("#999999", "#84B237", "#6E98FF", "#B24932", "#F0E442")
+
+p <- ggplot(data, aes(x=factor(Label), y=F, fill=factor(Label))) + geom_boxplot()
 p = p + scale_x_discrete(xlab, labels=groups)
 p = p + scale_y_continuous(ylab, limits=c(0.35, 0.55))
 p = p + ggtitle(chart_title)
+p = p + scale_fill_manual(values=palette, guide=FALSE)
 p = p + theme_minimal()
 
-#png("boxplot.png")
 p # Draw that sucker
-#dev.off()
 ggsave("boxplot.png")

### 2014-08-02 paper/paper.tex
Added a neive bayes graph. Started shuffleing before partitionsing

@@
 \usepackage{graphicx}
-%\usepackage[margin=1.0in]{geometry}
+\usepackage{hyperref}
 \usepackage{float}
 \usepackage{setspace}
+\usepackage{fancyvrb}
 \usepackage[numbers]{natbib}
@@
 
-\begin{verbatim}
+\begin{Verbatim}[fontsize=\footnotesize]
   -3.176 excited==True and label is 'neutral'
@@
    1.515 2c==True and label is 'negative'
-\end{verbatim}
+\end{Verbatim}
 
@@
 
+\subsubsection{Support Vector Machine}
+
+%TODO
+
 \section{References}
@@
 
-\subsection{Implementation Source Code}
+\subsection{Running the Implementation}
+
+To acquire your own copy of the implementation discussed above. The following
+instructions are written for Ubuntu 14.04 GNU/Linux, however it should be able
+to run on any Unix-like system.
+
+\begin{enumerate}
+    \item \textbf{Download Source} - The source code is hosted on github.com
+        and can be viewed
+        \href{https://github.com/hockeybuggy/semantic\_eval}{here}. To download a zip
+        file and open it:
+
+\begin{Verbatim}[fontsize=\footnotesize]
+wget https://github.com/hockeybuggy/semantic_eval/archive/master.zip
+unzip master.zip
+cd master
+\end{Verbatim}
+% TODO test this and make a dist branch
+
+    \item \textbf{Install Prerequisites} - If \textit{python 2.7}, \textit{pip}, and \textit{flex} are not
+        installed, they can be installed easily via a package manger:
+\begin{Verbatim}[fontsize=\footnotesize]
+sudo apt-get install python2.7 pip flex
+\end{Verbatim}
+
+Then various required python packages can be installed with:
+\begin{Verbatim}[fontsize=\footnotesize]
+sudo pip install -r
+\end{Verbatim}
+% TODO make requirement file
+
+    \item \textbf{Compile Tokenizer} - The tokenizer is written in C for
+        performance reasons and can be compiled with:
+\begin{Verbatim}[fontsize=\footnotesize]
+make
+\end{Verbatim}
+
+    \item \textbf{Run the Program} - The classifier can be executed in a number of ways.
+There are two python programs that are executable: `conductor.py' and `crossval.py'.
+These two programs run the classifier in a simple fashion or with cross validation.
+There are a large number of command line arguments that can be viewed with:
+\begin{Verbatim}[fontsize=\footnotesize]
+python conductor -h
+\end{Verbatim}
+
+Since the command line arguments can be cumbersome many of the experiments can be run via the make file:
+
+\begin{Verbatim}[fontsize=\footnotesize]
+make tiny            # Quick running with only 100 examples
+make crossfolds-m000 # The MaxEnt baseline with cross-validation
+make crossfolds-m111 # MaxEnt with cross-validation & feature selection
+make crossfolds-b000 # The Naive Bayes baseline with cross-validation
+make crossfolds-b111 # Naive Bayes with cross-val & feature selection
+make crossfolds      # Run all of the cross-validation experiments
+\end{Verbatim}
+
+\end{enumerate}
 

### 2014-08-02 paper/figures/boxplot.R

@@ -1,19 +1,16 @@
 
 library(ggplot2)
 
-#data <- read.table("box.csv", header=TRUE, col.names=c("y"))
-#data <- read.table("box.csv", col.names=c("X", "F"))
-data <- read.csv("boxplot.csv", header=TRUE)
-
-print(data)
-
-chart_title <- "Maximum Entropy Classifier Performance"
 xlab <- "Experiment"
 ylab <- "F-score"
 groups <- c("All", "Just Stopwords", "Just Uncommon", "Just Normalization", "Baseline")
-
-cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
 palette <- c("#999999", "#84B237", "#6E98FF", "#B24932", "#F0E442")
+
+
+## Maxent boxplot
+data <- read.csv("maxent_boxplot.csv", header=TRUE)
+
+chart_title <- "Maximum Entropy Classifier 5-fold Performance"
 
 p <- ggplot(data, aes(x=factor(Label), y=F, fill=factor(Label))) + geom_boxplot()
 p = p + scale_x_discrete(xlab, labels=groups)
@@ -23,4 +20,21 @@ p = p + scale_fill_manual(values=palette, guide=FALSE)
 p = p + theme_minimal()
 
 p # Draw that sucker
-ggsave("boxplot.png")
+ggsave("maxent_boxplot.png")
+
+
+## Naive Bayes boxplot
+data <- read.csv("bayes_boxplot.csv", header=TRUE)
+
+chart_title <- "Naive Bayes Classifier 5-fold Performance"
+
+p <- ggplot(data, aes(x=factor(Label), y=F, fill=factor(Label))) + geom_boxplot()
+p = p + scale_x_discrete(xlab, labels=groups)
+p = p + scale_y_continuous(ylab, limits=c(0.35, 0.55))
+p = p + ggtitle(chart_title)
+p = p + scale_fill_manual(values=palette, guide=FALSE)
+p = p + theme_minimal()
+
+p # Draw that sucker
+ggsave("bayes_boxplot.png")
+

### 2014-08-02 src/crossval.py

@@ -80,16 +80,24 @@ def main(args):
     #return
 
     accumulation_dict = {}
+    if args.classifier_type == "max_ent":
+        validation = True
+    else:
+        validation = False
 
-    for i, fold in enumerate(generate_folds(partitions)):
+    for i, fold in enumerate(generate_folds(partitions, validation)):
         print "Fold number: {} looks like: {}".format(i, "".join(fold))
         #print fold
         print "Training fold", i
         train_set = select_set("t", fold, partitions)
         validation_set = select_set("v", fold, partitions)
         test_set = select_set("T", fold, partitions)
-        classifier = maxent_classifier_with_validation(train_set, validation_set,
+        if args.classifier_type == "max_ent":
+            classifier = maxent_classifier_with_validation(train_set, validation_set,
                     args.validation_metric, 3)
+        else:
+            train_set += validation_set
+            classifier = naive_bayes_classifier(train_set)
         print "Testing fold {}...".format(i),
         results_dict = classifier.test(test_set, args.labels, trace=False)
         #Add results to the accumulation dict
@@ -117,12 +125,18 @@ def select_set(set_type, fold, partitions):
     return output_set
 
 
-def generate_folds(partitions):
+def generate_folds(partitions, validation):
     num_folds = len(partitions)
-    if num_folds == 5:
-        sets = "tttvT"
-    elif num_folds == 10:
-        sets = "ttttttttvT"
+    if validation:
+        if num_folds == 5:
+            sets = "tttvT"
+        elif num_folds == 10:
+            sets = "ttttttttvT"
+    else:
+        if num_folds == 5:
+            sets = "ttttT"
+        elif num_folds == 10:
+            sets = "tttttttttT"
     available = {}
     #range(len(partitions))
     for order in permutations(sets, num_folds):

### 2014-08-02 src/split_dataset.py

@@ -25,6 +25,7 @@ def __call__(feature_list, test_size, validation_size=0.0):
 
 def partition(flist, n):
     outlist = []
+    random.shuffle(flist)
     splitsize = int(math.ceil(len(flist)/float(n)))
     for i in range(0, len(flist), splitsize):
         outlist.append(flist[i:i+splitsize])

### 2014-08-02 paper/paper.tex
Removed the old huge table

@@
     \begin{center}
-    \begin{tabular}{|c||c|c|c|c|r|r|r|r|}
+    \begin{tabular}{|r||c|c|}
         \hline
-                   & Classifier  & Stopwords & Uncommon  & Normalize & Run 1 & Run 2 & Run 3 & $\mu F$\\
+           Description    & mean F & std F  \\
         \hline
-        \textit{a} & MaxEnt      & Yes       & Yes       & Yes       & 51.55 & 52.80 & 54.09 & 52.81 \\
-        \textit{b} & \dots       & Yes       & Yes       & No        & 51.10 & 49.34 & 50.23 & 50.22 \\
-        \textit{c} & \dots       & Yes       & No        & Yes       & 53.51 & 51.97 & 52.06 & 52.51 \\
-        \textit{d} & \dots       & Yes       & No        & No        & 54.55 & 48.77 & 49.51 & 50.94 \\
-        \textit{e} & \dots       & No        & Yes       & Yes       & 50.88 & 50.55 & 52.09 & 51.17 \\
-        \textit{f} & \dots       & No        & Yes       & No        & 52.46 & 50.64 & 54.11 & 52.40 \\
-        \textit{g} & \dots       & No        & No        & Yes       & 49.80 & 56.26 & 54.13 & 53.40 \\
-        \textit{h} & \dots       & No        & No        & No        & 50.59 & 50.91 & 50.67 & 50.72 \\
-        \textit{i} & Naive Bayes & Yes       & Yes       & Yes       & 50.89 & 50.34 & 51.64 & 50.96 \\
-        \textit{j} & \dots       & Yes       & Yes       & No        & 48.56 & 46.99 & 51.01 & 48.85 \\
-        \textit{k} & \dots       & Yes       & No        & Yes       & 51.55 & 51.22 & 49.79 & 50.85 \\
-        \textit{l} & \dots       & Yes       & No        & No        & 47.03 & 50.45 & 49.01 & 48.83 \\
-        \textit{m} & \dots       & No        & Yes       & Yes       & 47.95 & 51.91 & 49.67 & 49.36 \\
-        \textit{n} & \dots       & No        & Yes       & No        & 47.88 & 50.02 & 48.78 & 48.89 \\
-        \textit{o} & \dots       & No        & No        & Yes       & 50.09 & 50.83 & 51.77 & 50.90 \\
-        \textit{p} & \dots       & No        & No        & No        & 51.15 & 50.05 & 47.27 & 49.49 \\
+           All            & 0.0   & 0.0    \\
+           Just Stopwords & 0.0    & 0.0    \\
+           Just Uncommon  & 0.0    & 0.0    \\
+           Just Normalize & 0.0    & 0.0    \\
+           Baseline       & 0.0    & 0.0    \\
         \hline
@@
     \end{center}
-    \caption{Results of variations on feature selection and training. The
-    `Citation' column indicates what type of classifier is being used. The
-    `Stopwords' column indicates if stop words have been removed. The `Uncommon'
-    column indicates if words with a document frequency lower than the threshold
-    (in this case more than one occurrence) have been removed. The `Normalize'
-    column indicates if the any steps have been taken to normalize features.}
+    \caption{Holla!}
     \label{table:results}
 \end{table}
+
+\begin{figure}[H]
+    \includegraphics{figures/maxent_boxplot.png}
+    \caption{Caption...}
+    \label{figure:maxent}
+\end{figure}
 

### 2014-08-03 paper/paper.tex
Added a section about cross validation. Included the second graph and fixed the cross validation

@@
 
-    %TODO talk about cross validation
-
 \end{enumerate}
@@
 baseline in terms of $F$. $F$ can be calculated as:
+
 \begin{equation}
@@
 
+\subsection{Smooth Performance Measurement}
+
+    Testing the performance of the system with a single run can produce skewed
+    results since whether `easy' Tweets end up in \textit{training set} or the
+    \textit{test set} will affect performance. To combat this the following
+    \textbf{exhaustive cross-validation} method is used:
+
+        \begin{enumerate}
+
+        \item \textbf{Partitioning} - The corpus of documents are shuffled and
+            separated into 5 or 10 sections.
+
+        \item \textbf{Folding} - The training and testing process are run
+            multiple times with sections used for various roles. The roles are
+            permuted so that the classifier is trained and tested with the
+            sections in all possible configurations. In each fold 60\% of the
+            partitions are designated as part of the \textit{training set},
+            20\% as the \textit{validation set}, and 20\% as the \textit{test set}.
+            Since the Naive Bayes classifier does not use a validation set
+            40\% of the partitions are designated as part of the \textit{test set}
+
+            %TODO is this clear?
+
+        \begin{enumerate}
+
+            \item \textbf{Training} - The classifier is trained with the
+                partitions designated as part of the \textit{training set} for
+                the fold. The Maximum Entropy classifier also uses the
+                \textit{validation set} to determine when to stop the training
+                process.
+
+            \item \textbf{Testing} - The performance of the classifier is
+                evaluated using the \textit{test set} and the results are recorded.
+
+        \end{enumerate}
+
+        \item \textbf{Aggregating} - The results from all folds are averaged.
+
+        \end{enumerate}
+
 \subsection{Baseline}
@@
 The baseline for this project is established by running the Maximum Entropy
-classifier without any Stop word removal, Uncommon word removal, Or feature
-Normalization. The F-score that is achieved is 50.72. See Experiment \textit{g}
-in Table \ref{table:results} to see the results in context.
+classifier without any stopword removal, uncommon word removal, Or feature
+normalization. The F-score that is achieved is 50.72. See Experiment \textit{g}
+in Table \ref{table:maxent-results} to see the results in context.
+
+\subsection{Number of features}
+
+Number of features retained varies from Tweet to Tweet. To summarize the number
+of features retained after different process Table \ref{table:numfeatures}
+presents the mean number of features per Tweet for positive, neutral, negative
+examples as well as an overall average.
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{|c||r|r|r|r|r|}
+        \hline
+        Description        & Positive & Neutral & Negative & Overall & Total \\
+        \hline
+        All                & 14.85    & 14.06   & 15.10    & 14.49   & 5964 \\
+        Just Stopwords     & 15.95    & 15.40   & 16.33    & 15.73   & 0 \\
+        Just Uncommon      & 18.54    & 17.81   & 18.82    & 18.22   & 5993 \\
+        Just Normalization & 19.64    & 19.15   & 20.05    & 19.46   & 0 \\
+        Baseline           & 20.65    & 20.45   & 20.96    & 20.58   & 0 \\
+        \hline
+    \end{tabular}
+    \end{center}
+    \caption{`Positive', `Neutral', `Negative', and `Overall' refer to the
+    average number of features per Tweet in each experiment. `Total' refers to
+    the total number of different features in the dataset}
+    \label{table:numfeatures}
+\end{table}
 
@@
 
-Since the \textit{test set} is random subset of the corpus, the results of the
-classifier can vary slightly between runs. In order to effectively evaluate the
-performance of the classifier under certain conditions each experiment is
-conducted 3 times and averaged.
+\subsubsection{Maximum Entropy Classifier}
 
@@
     \end{center}
-    \caption{Holla!}
-    \label{table:results}
+    \caption{Performance of the Maximum Entropy classifier using exhaustive
+    cross-validation with 5 partitions}
+    \label{table:maxent-results}
 \end{table}
@@
 \begin{figure}[H]
-    \includegraphics{figures/maxent_boxplot.png}
+    \begin{center}
+    \includegraphics[scale=0.75]{figures/maxent_boxplot.png}
     \caption{Caption...}
     \label{figure:maxent}
+    \end{center}
 \end{figure}
 
-The results in Table \ref{table:results} indicates that there is not lot of
-difference variation between experiments. The best average F-score is
-experiment \textit{g}, however $\sigma_{g} = 2.69$. In contrast, the second
-best F-score is experiment \textit{a} exhibits more consistent classification
-with $\sigma_{a} = 1.04$.
-
-Number of features retained varies from Tweet to Tweet. To summarize the number
-of features retained after different process Table \ref{table:numfeatures}
-presents the mean number of features per Tweet for positive, neutral, negative
-examples as well as an overall average.
+\subsubsection{Naive Bayes Classifier}
 
@@
     \begin{center}
-    \begin{tabular}{|c||r|r|r|r|r|}
+    \begin{tabular}{|r||c|c|}
         \hline
-                               & Positive & Neutral & Negative & Overall & Total \\
+           Description    & mean F & std F \\
         \hline
-        \textit{a}, \textit{i} & 14.85    & 14.06   & 15.10    & 14.49   & 5964 \\
-        \textit{b}, \textit{j} & 14.91    & 14.30   & 15.30    & 14.67   & 7493 \\
-        \textit{c}, \textit{k} & 15.95    & 15.40   & 16.33    & 15.73   & 0 \\
-        \textit{d}, \textit{l} & 17.13    & 16.86   & 17.41    & 17.04   & 0 \\
-        \textit{e}, \textit{m} & 18.54    & 17.81   & 18.82    & 18.22   & 5993 \\
-        \textit{f}, \textit{n} & 18.43    & 17.87   & 18.85    & 18.21   & 7522 \\
-        \textit{g}, \textit{o} & 19.64    & 19.15   & 20.05    & 19.46   & 0 \\
-        \textit{h}, \textit{p} & 20.65    & 20.45   & 20.96    & 20.58   & 0 \\
+           All            & 0.0    & 0.0   \\
+           Just Stopwords & 0.0    & 0.0   \\
+           Just Uncommon  & 0.0    & 0.0   \\
+           Just Normalize & 0.0    & 0.0   \\
+           Baseline       & 0.0    & 0.0   \\
         \hline
@@
     \end{center}
-    \caption{`Positive', `Neutral', `Negative', and `Overall' refer to the
-    average number of features per Tweet in each experiment. `Total' refers to
-    the total number of different features in the dataset}
-    \label{table:numfeatures}
+    \caption{Performance of the Naive Bayes classifier using exhaustive
+    cross-validation with 5 partitions}
+    \label{table:bayes-results}
 \end{table}
+
+\begin{figure}[H]
+    \begin{center}
+    \includegraphics[scale=0.75]{figures/bayes_boxplot.png}
+    \caption{Caption...}
+    \label{figure:bayes}
+    \end{center}
+\end{figure}
 

### 2014-08-03 src/crossval.py

@@ -131,12 +131,12 @@ def generate_folds(partitions, validation):
         if num_folds == 5:
             sets = "tttvT"
         elif num_folds == 10:
-            sets = "ttttttttvT"
+            sets = "ttttttvvTT"
     else:
         if num_folds == 5:
-            sets = "ttttT"
+            sets = "tttTT"
         elif num_folds == 10:
-            sets = "tttttttttT"
+            sets = "ttttttTTTT"
     available = {}
     #range(len(partitions))
     for order in permutations(sets, num_folds):

### 2014-08-04 paper/paper.tex
Fixed the results for the maximum entropy classifier. Filled out the tables

@@
 
+\subsection{Number of features}
+
+Number of features retained after feature selection varies from Tweet to Tweet.
+To summarize the number of features retained after different process Table
+\ref{table:numfeatures} presents the mean number of features per Tweet for
+positive, neutral, negative examples as well as an overall average.
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{|c||r|r|r|r|}
+        \hline
+        Description        & Positive & Neutral & Negative & Overall \\
+        \hline
+        All                & 14.85    & 14.06   & 15.10    & 14.49 \\
+        Just Stopwords     & 17.13    & 16.86   & 17.41    & 17.04 \\
+        Just Uncommon      & 18.43    & 17.87   & 18.85    & 18.21 \\
+        Just Normalization & 19.65    & 19.16   & 20.06    & 19.46 \\
+        Baseline           & 20.65    & 20.45   & 20.96    & 20.58 \\
+        \hline
+    \end{tabular}
+    \end{center}
+    \caption{`Positive', `Neutral', `Negative', and `Overall' refer to the
+    average number of features per Tweet in each experiment.}
+    \label{table:numfeatures}
+\end{table}
+
+As presented in Table \ref{table:numfeatures}, the number of features decreases
+each time a feature set simplification method is turned on. Normalization does
+not appear to significantly reduce the number of features per Tweet. This make
+sense because the number of features in would only be reduced if it contained
+tokens that were different before simplification and were the same after (e.g.
+A Tweet that contained `2' and `3' before normalization would only contain the
+feature `\#NUM' after normalization).
+
 \subsection{Baseline}
@@
 classifier without any stopword removal, uncommon word removal, Or feature
-normalization. The F-score that is achieved is 50.72. See Experiment \textit{g}
-in Table \ref{table:maxent-results} to see the results in context.
-
-\subsection{Number of features}
-
-Number of features retained varies from Tweet to Tweet. To summarize the number
-of features retained after different process Table \ref{table:numfeatures}
-presents the mean number of features per Tweet for positive, neutral, negative
-examples as well as an overall average.
-
-\begin{table}[H]
-    \begin{center}
-    \begin{tabular}{|c||r|r|r|r|r|}
-        \hline
-        Description        & Positive & Neutral & Negative & Overall & Total \\
-        \hline
-        All                & 14.85    & 14.06   & 15.10    & 14.49   & 5964 \\
-        Just Stopwords     & 15.95    & 15.40   & 16.33    & 15.73   & 0 \\
-        Just Uncommon      & 18.54    & 17.81   & 18.82    & 18.22   & 5993 \\
-        Just Normalization & 19.64    & 19.15   & 20.05    & 19.46   & 0 \\
-        Baseline           & 20.65    & 20.45   & 20.96    & 20.58   & 0 \\
-        \hline
-    \end{tabular}
-    \end{center}
-    \caption{`Positive', `Neutral', `Negative', and `Overall' refer to the
-    average number of features per Tweet in each experiment. `Total' refers to
-    the total number of different features in the dataset}
-    \label{table:numfeatures}
-\end{table}
+normalization. The F-score that is achieved is 50.72.
 
@@
     \begin{center}
-    \begin{tabular}{|r||c|c|}
+    \begin{tabular}{|r||c|c|c|}
         \hline
-           Description    & mean F & std F \\
+        Description    & $\mu F$ & $\sigma F$ & $\delta\ \mu F$ \\
         \hline
-           All            & 0.0    & 0.0   \\
-           Just Stopwords & 0.0    & 0.0   \\
-           Just Uncommon  & 0.0    & 0.0   \\
-           Just Normalize & 0.0    & 0.0   \\
-           Baseline       & 0.0    & 0.0   \\
+        All            & \textbf{50.96} & 1.93 &  2.59 \\
+        Just Stopwords & 48.27   & 1.83 & -0.10 \\
+        Just Uncommon  & 49.02   & 1.96 &  0.65 \\
+        Just Normalize & 49.55   & 2.10 &  1.18 \\
+        Baseline       & 48.37   & 2.15 & - \\
         \hline
@@
     \begin{center}
-    \begin{tabular}{|r||c|c|}
+    \begin{tabular}{|r||c|c|c|}
         \hline
-           Description    & mean F & std F \\
+        Description    & $\mu F$ & $\sigma F$ & $\delta\ \mu F$ \\
         \hline
-           All            & 0.0    & 0.0   \\
-           Just Stopwords & 0.0    & 0.0   \\
-           Just Uncommon  & 0.0    & 0.0   \\
-           Just Normalize & 0.0    & 0.0   \\
-           Baseline       & 0.0    & 0.0   \\
+        All            & 49.28  & 0.81 &  1.17 \\
+        Just Stopwords & 47.29  & 0.76 & -0.82 \\
+        Just Uncommon  & 48.34  & 1.11 &  0.23 \\
+        Just Normalize & \textbf{49.44} & 1.00 & 1.33\\
+        Baseline       & 48.11  & 0.74 & - \\
         \hline
@@
 
-% TODO finish table
-
 % TODO Student T-test
-
-As presented in Table \ref{table:numfeatures}, the number of features decreases
-each time a feature set simplification method is turned on. Normalization does
-not appear to significantly reduce the number of features per Tweet. This make
-sense because the number of features in would only be reduced if it contained
-tokens that were different before simplification and were the same after (e.g.
-A Tweet that contained `2' and `3' before normalization would only contain the
-feature `\#NUM' after normalization).
 
@@
 
-%TODO talk about the features
+The implementation create for this project has the ability to show which
+features are the most discriminatory. The following is a list of the top 30
+most informative features from one run of the Maximum Entropy classifier:
 
@@
 \end{Verbatim}
+
+Some of the features listed above make perfect sense, such as `excited' not
+being associated with the neutral class and `shitty' being associated with the
+negative class. However some of the most discriminating features appear in the
+dataset just enough to get past the uncommon word cutoff, such as `calvin' and
+`oneil'.
 

### 2014-08-04 paper/paper.tex
Added labels. Wrote some for the intro and background. Stubed out some TODOs

@@
 
-July 29th, 2014 %TODO fix this
+August 4th, 2014 %TODO fix this
 
@@
 \section{Introduction}
+\label{section:intro}
 
@@
 \subsection{Specific Problem}
+\label{ssection:specificproblem}
 
@@
 mistakes and inconsistent grammar then other sources of text. Tweets often also
-contain links to other websites in the form of URLs as well as taging system
-for topics and other users.
+contain URLs to other websites. Tweets also contain a certain amount of OOV
+(Out-Of-Vocabulary) words, such as Hashtags, a tagging system for topics
+allowing Tweets in a similar vein of conversation to be found. Other OOV words
+include mentions (e.g. `@BarackObama') which are a method to direct a tweet to
+one or more users, as well as `RT' which is an acronym for `retweet'
+communicating that this particular Tweet is a reissuing of another users Tweet.
+Another issue that is out of the scope of this project is that Twitter
+currently supports 35+ languages, meaning that in-order to determine the
+sentiment most systems must first determine which language the tweet is in.
 
 \subsection{Task Description}
+\label{ssection:taskdescription}
 
@@
 Message polarity classification. The organizers used the Amazon service
-``Mechanical Turk" to get many humans to annotate Tweets as `positive',
-`negative' or `neutral'. In tweets with mixed sentiments, the prevailing
-sentiment was chosen. Participants were tasked with creating a classifier to
-establish labels for Tweets not in the training dataset. The various
-submissions of the participants were then evaluated by the average of the
-F-positive and the F-negative. The submissions were allowed categorized as
+``Mechanical Turk" to get many humans to annotate English language Tweets as
+`positive', `negative' or `neutral'. In Tweets with mixed sentiments, the
+prevailing sentiment was chosen. Participants were tasked with creating a
+classifier to establish labels for Tweets not in the training dataset. The
+various submissions of the participants were then evaluated by the average of
+the F-positive and the F-negative. The submissions were allowed categorized as
 `unconstrained' or `constrained' depending on if they did or did not use
@@
 \section{Background}
+\label{section:background}
 
@@
 few years \cite{Jianfeng2013} \cite{Barbosa2010} \cite{Gokulakrishnan2012}.
-Many previous attempts researched make use of Native Bayes, Maximum Entropy,
-and SVM classifiers.
+Sentiment analysis has been very closely linked with opinion mining, which is
+the practice of extracting sentiment on a particular topic in order to gain
+insights into public opinion on the topic.
+
+According to `Opinion mining and sentiment analysis' \cite{Pang2008}: ``The
+year 2001 or so seems to mark the beginning of widespread awareness of the
+research problems that sentiment analysis and opinion mining raise''. This
+explosion in research has happened very recently, and as such the field is
+moving very quickly.
+
+Many previous attempts researched make use of Naive Bayes, Maximum Entropy, and
+SVM classifiers. The Naive Bayes classifier uses the occurrences of features in
+the \textit{training set} to calculate the probability that an example in the
+\textit{test set} belongs in a given class. This method has the benefit of
+linear time training since there is no iterative process, but I makes the
+assumption that all features are independent, which is not the case in natural
+language. The Maximum Entropy approach is explained in detail in section
+\ref{ssection:summaryofmaxent}.
 
@@
 
-\textit{Note: This section needs to be expanded. I am just not sure what else to write about...}
-
 \section{Our Implementation}
+\label{section:implementation}
 
 \subsection{Summary of Maximum Entropy}
+\label{ssection:summaryofmaxent}
 
 The Maximum Entropy classification method was focused on due to the limited
-duration of the project. This supervised machine learning method calculates the
-probability that a given document $d$ belongs to the class $c$.  The Maximum
-Entropy approach is summarized below. For a more detailed description, see:
-Nigam et al. \cite{Nigam1999}.
+duration of the project, however a Naive Bayes classifier was also implemented
+to provide a point of comparison. This supervised machine learning method
+calculates the probability that a given document $d$ belongs to the class $c$.
+The Maximum Entropy approach is summarized below. For a more detailed
+description, see: Nigam et al. \cite{Nigam1999}.
 
@@
 \subsection{Preprocessing and Feature Selection}
+\label{ssection:featureselection}
+
+% TODO expand on document frequency
 
@@
 \subsection{Training Optimization}
+\label{ssection:optimization}
 
@@
 \section{Experiments and Discussion}
+\label{section:experiments}
 
 \subsection{Dataset}
+\label{ssection:dataset}
 
@@
 
+%TODO add example
+
 \subsection{Evaluation Measures}
+\label{ssection:evaluation}
 
@@
 
-\subsection{Smooth Performance Measurement}
+\subsection{Improving Performance Measurement}
+\label{ssection:performancemeasurement}
 
@@
 \subsection{Number of features}
+\label{ssection:numfeatures}
 
@@
 \subsection{Baseline}
+\label{ssection:baseline}
 
@@
 \subsection{Experimental Results}
+\label{ssection:results}
+
+%TODO write something here about the method
 
@@
 \end{table}
+
+% TODO Write something here about uncommon not getting performance gains
+% without normalization
 
@@
 \subsection{Most Informative Features}
+\label{ssection:informativefeatures}
 
@@
 \subsection{Comparison to Other Systems}
+\label{ssection:comparison}
 
@@
 \end{table}
+%TODO fix this table
 
 \section{Conclusions and Future Work}
+\label{section:conclusionsandfuturework}
 
 \subsection{Conclusions}
+\label{ssection:conclusions}
 
@@
 \subsection{Future Work}
+\label{ssection:futurework}
 
 \subsubsection{Hashtags}
+\label{sssection:hashtags}
 
@@
 \subsubsection{Users}
+\label{sssection:users}
 
@@
 \subsubsection{Support Vector Machine}
+\label{sssection:svm}
 
@@
 \section{References}
+\label{section:referances}
 
@@
 \section{Appendices}
+\label{section:appendices}
 
 \subsection{Running the Implementation}
+\label{ssection:runningtheimplementation}
 
@@
 
-    \item \textbf{Install Prerequisites} - If \textit{python 2.7}, \textit{pip}, and \textit{flex} are not
-        installed, they can be installed easily via a package manger:
+    \item \textbf{Install Prerequisites} - If \textit{python 2.7},
+        \textit{pip}, and \textit{flex} are not installed, they can be
+        installed easily via a package manger:
+
 \begin{Verbatim}[fontsize=\footnotesize]
@@
 Then various required python packages can be installed with:
+
 \begin{Verbatim}[fontsize=\footnotesize]
-sudo pip install -r
+sudo pip install numpy nltk
 \end{Verbatim}
-% TODO make requirement file
 
@@
 
-    \item \textbf{Run the Program} - The classifier can be executed in a number of ways.
-There are two python programs that are executable: `conductor.py' and `crossval.py'.
-These two programs run the classifier in a simple fashion or with cross validation.
-There are a large number of command line arguments that can be viewed with:
+    \item \textbf{Run the Program} - The classifier can be executed in a number
+        of ways. There are two python programs that are executable:
+        `conductor.py' and `crossval.py'. These two programs run the classifier
+        in a simple fashion or with cross validation. There are a large number
+        of command line arguments that can be viewed with:
+
 \begin{Verbatim}[fontsize=\footnotesize]
@@
 
-Since the command line arguments can be cumbersome many of the experiments can be run via the make file:
+Since the command line arguments can be cumbersome many of the experiments can
+be run via the make file:
 

### 2014-08-04 paper/paper.tex
Wrote a readme in preperation of making this repo public
Wrote a whole bunch more for the background. Included an example tweet in the dataset

@@
 allowing Tweets in a similar vein of conversation to be found. Other OOV words
-include mentions (e.g. `@BarackObama') which are a method to direct a tweet to
+include mentions (e.g. `@BarackObama') which are a method to direct a Tweet to
 one or more users, as well as `RT' which is an acronym for `retweet'
@@
 currently supports 35+ languages, meaning that in-order to determine the
-sentiment most systems must first determine which language the tweet is in.
+sentiment most systems must first determine which language the Tweet is in.
 
@@
 
-Quite a bit of research has been done in the field of sentiment analysis
-recently. Much of the work has involved data from other contexts such as Movie
-reviews \cite{Pang2002}, and blog posts \cite{Melville2009}. The challenges
-associated with classifying Twitter data has attracted researchers in the past
-few years \cite{Jianfeng2013} \cite{Barbosa2010} \cite{Gokulakrishnan2012}.
-Sentiment analysis has been very closely linked with opinion mining, which is
-the practice of extracting sentiment on a particular topic in order to gain
-insights into public opinion on the topic.
-
-According to `Opinion mining and sentiment analysis' \cite{Pang2008}: ``The
+According to `Opinion Mining and Sentiment Analysis' \cite{Pang2008}: ``The
 year 2001 or so seems to mark the beginning of widespread awareness of the
@@
 explosion in research has happened very recently, and as such the field is
-moving very quickly.
+moving very quickly. Much of the earlier work in the field involved data from
+other contexts such as Movie reviews \cite{Pang2002}, and blog posts
+\cite{Melville2009}. The challenges associated with classifying Twitter data
+has only attracted researchers in the past few years \cite{Jianfeng2013}
+\cite{Barbosa2010} \cite{Gokulakrishnan2012}.
 
-Many previous attempts researched make use of Naive Bayes, Maximum Entropy, and
+Sentiment analysis is a very specific type of \textbf{text classification}, a problem
+that is well summarized in chapter 6 of \textit{Mining Text Data} by Aggarwal
+and Zhai \cite{Aggarwal2012} as:
+
+\begin{quote}
+    We have a set of training records $\mathcal{D} = \{X_{1} , . . .\ , X_{N}
+    \}$, such that each record is labeled with a class value drawn from a set
+    of k different discrete values indexed by $\{1 . . . k\}$. The training
+    data is used in order to construct a classification model, which relates
+    the features in the underlying record to one of the class labels.
+\end{quote}
+
+In the case of sentiment analysis the class labels being applied to the records
+denote the attitude or opinion in the text. The focus of this project is
+determining sentiment at the document level which assumes that the document
+expresses a predominate sentiment. This is a somewhat reasonable assumption
+given the fact that Tweets are limited in size, making it difficult to express
+mixed sentiment. Sentiment analysis is very closely linked with opinion mining,
+which is the practice of extracting sentiment on a particular topic in order to
+gain insights into public opinion on the topic.
+
+Much of the previous research make use of Naive Bayes, Maximum Entropy, and
 SVM classifiers. The Naive Bayes classifier uses the occurrences of features in
@@
 language. The Maximum Entropy approach is explained in detail in section
-\ref{ssection:summaryofmaxent}.
+\ref{ssection:summaryofmaxent}. While Maximum Entropy and Naive Bayes are both
+probabilistic approaches the to problem, Support Vector Machine (SVM)
+classifiers take a different approach to the problem. ``SVM Classifiers attempt
+partition the data space with the use of linear or non-linear delineations
+between the different classifiers.''\cite{Aggarwal2012}.
 
-%TODO Sentiment Analysis
-%TODO Text Classification
 %TODO Feature Selection
@@
 label that conveys neutral sentiment. This neutral label is one of `neutral',
-`objective', or `objective-OR-neutral'.
+`objective', or `objective-OR-neutral'. The following is an example of a
+positive Tweet:
 
-%TODO add example
+\begin{Verbatim}[fontsize=\footnotesize]
+"positive", "Gas by my house hit $3.39!!!! I'm going to Chapel Hill on Sat. :)"
+\end{Verbatim}
 
@@
 
-Nearly all Twitter users have published more than one tweet. A more advanced
+Nearly all Twitter users have published more than one Tweet. A more advanced
 classifier could establish a particular users propensity to publishing a
-prevailing sentiment in all of their tweets.
+prevailing sentiment in all of their Tweets.
 
@@
 sentiment. For a hypothetical example, Tweets addressed to Emma Watson
-(`@EmWatson') are more likely to have a positive sentiment, while tweets to
+(`@EmWatson') are more likely to have a positive sentiment, while Tweets to
 Barack Obama (`@BarackObama') may contain extremely mixed sentiment.
@@
 \end{Verbatim}
+
 % TODO test this and make a dist branch

### 2014-08-04 paper/paper.tex
Wrote about the results a bit

@@
 %TODO Feature Selection
+%TODO mention bag of words
 
@@
 
-\subsection{Number of features}
+\subsection{Baseline}
+\label{ssection:baseline}
+
+The baseline for this project is established by running the Maximum Entropy
+classifier without any stopword removal, uncommon word removal, Or feature
+normalization. The F-score that is achieved is \textbf{50.72}.
+
+%TODO consider cleaning the text up here
+
+\subsection{Experimental Results}
+\label{ssection:results}
+
+The following experiments examine the results of the Maximum Entropy classifier
+and the Naive Bayes classifier with various feature selection methods turned on
+or off. The `Baseline' experiment refers to no feature selection. The `Just
+Stopwords' experiment refers the only removing stopwords. The `Just Uncommon'
+experiment refers to only removing words with a document frequency of one. The
+`Just Normalization' experiment refers to only applying feature normalization
+mechanisms. The `All' experiment refers to testing the classifier with all of
+the previous feature selection methods turned on.
+
+%TODO add references to the feature selection section
+
+\subsubsection{Number of features}
 \label{ssection:numfeatures}
@@
 
+%TODO check these results
+
 As presented in Table \ref{table:numfeatures}, the number of features decreases
@@
 
-\subsection{Baseline}
-\label{ssection:baseline}
-
-The baseline for this project is established by running the Maximum Entropy
-classifier without any stopword removal, uncommon word removal, Or feature
-normalization. The F-score that is achieved is 50.72.
-
-\subsection{Experimental Results}
-\label{ssection:results}
-
-%TODO write something here about the method
+%TODO clarify
 
@@
 \end{table}
+
+As Table \ref{table:maxent-results} shows `All' experiment provides the best
+results over the baseline. The `Just Stopwords' experiment actually provides
+slightly worse results then the baseline indicating that in context of Tweets
+with so few features in each example every feature counts. The `Just Uncommon'
+experiment does not provide very significant gains when used alone. This is
+potentially due to the fact that with out normalization turned, features such
+as `just' are `Just' are determined to be different and may be removed if each
+only occur once.
 
@@
         NTNU       & 53.23 \\
-        \textbf{Best MaxEnt}& \textbf{52.81} \\
         UoM        & 51.81 \\
-        \textbf{Best Navie Bayes}& \textbf{50.96} \\
+        \textbf{MaxEnt}& \textbf{50.96} \\
         SSA-UO     & 50.17 \\
@@
 \end{table}
-%TODO fix this table
+%TODO add naive bayes
 
@@
 
+\subsection{Stopword list}
+\label{ssection:stopwords}
+
+The list of stopwords was acquired at \href{holla}{www.ranks.nl/stopwords} and
+is as follows:
+
+a, about, an, are, as, at, be, by, com, for, from, how, in, is, it, of, on, or,
+that, the, this, to, was, what, when, where, who, will, with
+
 \end{document}

### 2014-08-04 paper/paper.tex
Wrote a bunch for future work

@@
 
-Sentiment analysis is a very specific type of \textbf{text classification}, a problem
-that is well summarized in chapter 6 of \textit{Mining Text Data} by Aggarwal
-and Zhai \cite{Aggarwal2012} as:
+Sentiment analysis is a very specific type of \textbf{text classification}, a
+problem that is well summarized in chapter 6 of \textit{Mining Text Data} by
+Aggarwal and Zhai \cite{Aggarwal2012} as:
 
@@
 
-%TODO Feature Selection
-%TODO mention bag of words
+In order to perform text classification of any kind one of the most important
+aspects is deciding how to represent a document and how to select
+representative features. A document is often represented as either a
+\textit{bag-of-words} or \textit{string}. For the limited time frame of this
+project the \textit{bag-of-words} method was used.
+
+There are many established methods of selecting features such as document
+frequency, which is simply the number of documents that a word occurs at least
+once in. Document frequency has the added benefit of not requiring a class
+labels to select features. While document frequency is the only method employed
+for this project many other method exist, such as Gini Index, Information Gain,
+and $\chi^{2}$-statistic \cite{Aggarwal2012}. Each of these more complex
+methods rely on the class label in the training set in order to determine how
+well the feature discriminates between classes.
 
@@
 \label{ssection:featureselection}
-
-% TODO expand on document frequency
 
@@
                 discriminate between classes are eliminated. Because of the
-                limited size of the dataset only 28 stopwords are used.
+                limited size of the dataset only 28 stopwords are used. For a
+                full list of stopwords see section \ref{ssection:stopwords}
 
@@
                 likely to cause the classifier to overfit to the training set.
+                A threshold of one was used throughout the testing process.
 
@@
 
-% TODO Write something here about uncommon not getting performance gains
-% without normalization
-
 \begin{figure}[H]
@@
     \includegraphics[scale=0.75]{figures/maxent_boxplot.png}
-    \caption{Caption...}
+    \caption{This boxplot shows the F-score of each of twenty folds in all five
+    Maximum Entropy experiments}
     \label{figure:maxent}
@@
     \includegraphics[scale=0.75]{figures/bayes_boxplot.png}
-    \caption{Caption...}
+    \caption{This boxplot shows the F-score of each of ten folds in all five
+    Naive Bayes experiments}
     \label{figure:bayes}
@@
 
+The top solution from the National Research Council of Canada made use of a
+Hashtag lexicon that they developed between April of 2012 and December of the
+same year \cite{Mohammad2013}. The final \textit{NRC Hashtag Sentiment Lexicon}
+has more than 350,00 entries and is available at
+\href{http://www.saifmohammad.com/WebDocs/NRC-Hashtag-Sentiment-Lexicon-v0.1.zip}{Saif
+Mohammad's website}.
+
 \subsubsection{Users}
@@
 
+\subsubsection{Negation}
+\label{sssection:negation}
+%TODO
+\subsubsection{N-gram Features}
+\label{sssection:ngram}
+%TODO
+\subsubsection{Employing Sentiment Lexicon}
+\label{sssection:sentimentlexicon}
+
+Many of the more complex solutions submitted to the SemEval-2013 workshop made
+uses of sentiment lexicons that capture a term's polarity. These lexicons, such
+as \href{http://sentiwordnet.isti.cnr.it/}{SentiWordNet}, express the positive,
+neutral, and negative sentiment of each homonym.
+
 \subsubsection{Support Vector Machine}
@@
 
-%TODO
+Many of the top solutions submitted to the workshop such as NRC-Canada
+\cite{Mohammad2013} made use of a support vector machine for classification.
+This indicates that when used effectively a SVM solution can out-perform a
+Maximum Entropy solution. The KLUE team on the other hand found that their
+Maximum Entropy solution outperform their linear SVM solution
+\cite{Proisl2013}.
 

### 2014-08-05 src/crossval.py
Fixed the number of iterations with cross validation

@@ -92,12 +92,15 @@ def main(args):
         train_set = select_set("t", fold, partitions)
         validation_set = select_set("v", fold, partitions)
         test_set = select_set("T", fold, partitions)
-        if args.classifier_type == "max_ent":
+
+        if args.validation_metric != "none":
             classifier = maxent_classifier_with_validation(train_set, validation_set,
                     args.validation_metric, 3)
+        elif args.numIterations:
+            classifier = maxent_classifier(train_set, iterations=args.numIterations)
         else:
-            train_set += validation_set
             classifier = naive_bayes_classifier(train_set)
+
         print "Testing fold {}...".format(i),
         results_dict = classifier.test(test_set, args.labels, trace=False)
         #Add results to the accumulation dict

### 2014-08-05 paper/paper.tex
Added a new graph but the data for it is not done. Also worked on the future work section

@@
 The baseline for this project is established by running the Maximum Entropy
-classifier without any stopword removal, uncommon word removal, Or feature
-normalization. The F-score that is achieved is \textbf{50.72}.
-
-%TODO consider cleaning the text up here
+classifier without any stopword removal, uncommon word removal (words with a
+document frequancy > 1), Or feature normalization. The F-score that is achieved
+is \textbf{50.72}.
 
@@
 the previous feature selection methods turned on.
-
-%TODO add references to the feature selection section
 
@@
 \label{sssection:negation}
-%TODO
+
+One problem with the current implementation is that it lack support for
+negation. In it's current form the classifier would likely misunderstand the
+sequence ``not perfect'' since `not' is a vaguely negative word and `perfect'
+is a very positive word, it would likely be classified as positive when in fact
+the sentiment is quite clearly negative. A common approach to this problem is
+to add a suffix (such as "\_NEG") to word that appear between a negation word
+and a section delimiting punctuation mark (such as `,', `.', `:', `;', `!',
+`?'). By separating negated features from their non-negated instances, features
+can do a better job of distinguishing classes.
+
 \subsubsection{N-gram Features}
 \label{sssection:ngram}
-%TODO
+
+One way that many of the other bag-of-words solutions capture word order is by
+creating features consisting of sequences of words called bigrams. Adding
+bigram features adds a large number of features which can add complexity to
+training. This concept can also be extended to sequences of length n, called
+ngrams.
+
+The added complexity associated with ngrams did not deter the National Research
+Council of Canada from using ngrams of length 1, 2, 3, and 4 as well as
+`non-contiguous' ngrams which are described as `ngrams with one token replaced
+by *' \cite{Mohammad2013}.
+
 \subsubsection{Employing Sentiment Lexicon}
@@
 
-Many of the more complex solutions submitted to the SemEval-2013 workshop made
+Most of the more complex solutions submitted to the SemEval-2013 workshop made
 uses of sentiment lexicons that capture a term's polarity. These lexicons, such

### 2014-08-05 paper/figures/overfitting.R

@@ -1,0 +1,23 @@
+
+library(ggplot2)
+
+xlab <- "Number of Iterations"
+ylab <- "F-score"
+
+
+## Maxent boxplot
+data <- read.csv("overfitting.csv", header=TRUE)
+
+chart_title <- "Maximum Entropy Classifier Performance"
+
+p <- ggplot(data, aes(x=NumIter, y=F)) + geom_point()
+p = p + geom_smooth(method="loess")
+p = p + scale_x_continuous(xlab)
+p = p + scale_y_continuous(ylab, limits=c(0.35, 0.55))
+p = p + ggtitle(chart_title)
+#p = p + scale_fill_manual(values=palette, guide=FALSE)
+p = p + theme_minimal()
+
+p # Draw that sucker
+ggsave("overfitting.png")
+

### 2014-08-05 paper/paper.tex
Wrote a conclusion. It needs some work

@@
         \hline
-        Majority Baseline & 29.19 \\
-        \hline
     \end{tabular}
@@
 
-\textit{Note: I would like to finish the results section before I start this section }
-
-%TODO get a stronger conclusion
+As shown in Table \ref{table:comparison} there is a lot of room for improvement
+before this system is a completive solution. However, only simple methods have
+been employed including: stopword removal of only 28 words, words with a
+document frequency lower than one removed, and normalization of words, emoticons,
+and OOV words. These simple preprocessing and feature selection methods in
+combination with a Maximum Entropy classifier have demonstrated reasonable
+results.
 
@@
 
-The list of stopwords was acquired at \href{holla}{www.ranks.nl/stopwords} and
-is as follows:
+The list of stopwords was acquired \href{www.ranks.nl/stopwords}{here} and is
+as follows:
 

### 2014-08-05 paper/paper.tex
Made Meg's edits. Up to 18 pages

@@
 \usepackage{fancyvrb}
+\usepackage[font=footnotesize,labelfont=bf]{caption}
 \usepackage[numbers]{natbib}
@@
 
-Draft 3 %TODO ditch this
+Draft 4 %TODO ditch this
 
@@
 Social media allows people to discuss topics and disseminate their opinions
-with a near negligible cost. The low barrier of entry to social media allows
+with a near negligible cost. Social media's low barrier of entry allows
 everyone to share their opinions as much as they please. The scale of textual
@@
 
-Sentiment analysis is simply a classification task that attempts to label
-fragments of text that appropriately summarizes the attitude of the text.
-Natural Language Processing (NLP) provides a number of method for preforming
+Sentiment analysis is simply a classification task that attempts to correctly
+label fragments of text to appropriately summarizes the attitude of the text.
+Natural Language Processing (NLP) provides a number of method for performing
 sentiment analysis. Many of these methods, such as Naive Bayes and Maximum
@@
 
-The focus of this undergraduate research project has been to preform sentiment
+The focus of this undergraduate research project has been to perform sentiment
 analysis in data from the microbloging website Twitter. All of the messages,
@@
 many users of Twitter to use abbreviations and contractions. This data presents
-some interesting problems to performing good sentiment analysis due to it's
-short and informal nature. Twitter makes it extremely easy to publish a Tweet
-and has no way to edit a Tweet once published. This results in more spelling
-mistakes and inconsistent grammar then other sources of text. Tweets often also
-contain URLs to other websites. Tweets also contain a certain amount of OOV
-(Out-Of-Vocabulary) words, such as Hashtags, a tagging system for topics
-allowing Tweets in a similar vein of conversation to be found. Other OOV words
-include mentions (e.g. `@BarackObama') which are a method to direct a Tweet to
-one or more users, as well as `RT' which is an acronym for `retweet'
+some interesting problems to performing good sentiment analysis due to the
+short and informal nature of the text. Twitter makes it extremely easy to
+publish a Tweet and has no way to edit a Tweet once published. This results in
+more spelling mistakes and inconsistent grammar then other sources of text.
+Tweets often also contain URLs to other websites. Tweets also contain a certain
+amount of OOV (Out-Of-Vocabulary) words, such as Hashtags, a tagging system for
+topics allowing Tweets in a similar vein of conversation to be found. Other OOV
+words include mentions (e.g. `@BarackObama') which are a method to direct a
+Tweet to one or more users, as well as `RT' which is an acronym for `retweet'
 communicating that this particular Tweet is a reissuing of another users Tweet.
 Another issue that is out of the scope of this project is that Twitter
-currently supports 35+ languages, meaning that in-order to determine the
+currently supports 35+ languages, meaning that in order to determine the
 sentiment most systems must first determine which language the Tweet is in.
@@
 various submissions of the participants were then evaluated by the average of
-the F-positive and the F-negative. The submissions were allowed categorized as
-`unconstrained' or `constrained' depending on if they did or did not use
-supplemental data, respectively.
+the F-positive and the F-negative (explained in depth in Section
+\ref{ssection:performancemeasurement}). The submissions were allowed
+categorized as `unconstrained' or `constrained' depending on if they did or did
+not use supplemental data, respectively.
 
@@
 
-In the case of sentiment analysis the class labels being applied to the records
-denote the attitude or opinion in the text. The focus of this project is
-determining sentiment at the document level which assumes that the document
+In the case of sentiment analysis, the class labels being applied to the
+records denote the attitude or opinion in the text. The focus of this project
+is determining sentiment at the document level, which assumes that the document
 expresses a predominate sentiment. This is a somewhat reasonable assumption
@@
 
-Much of the previous research make use of Naive Bayes, Maximum Entropy, and
-SVM classifiers. The Naive Bayes classifier uses the occurrences of features in
-the \textit{training set} to calculate the probability that an example in the
+Much of the previous research make use of Naive Bayes, Maximum Entropy, and SVM
+classifiers. The Naive Bayes classifier uses the occurrences of features in the
+\textit{training set} to calculate the probability that an example in the
 \textit{test set} belongs in a given class. This method has the benefit of
-linear time training since there is no iterative process, but I makes the
+linear time training since there is no iterative process, but it makes the
 assumption that all features are independent, which is not the case in natural
@@
 aspects is deciding how to represent a document and how to select
-representative features. A document is often represented as either a
-\textit{bag-of-words} or \textit{string}. For the limited time frame of this
-project the \textit{bag-of-words} method was used.
+representative features. A document is often represented as a
+\textit{bag-of-words}, which is defined a set of strings with no apparent
+order. The \textit{bag-of-words} method of representation was selected for this
+project.
 
@@
 labels to select features. While document frequency is the only method employed
-for this project many other method exist, such as Gini Index, Information Gain,
+for this project, many other methods exist, such as Gini Index, Information Gain,
 and $\chi^{2}$-statistic \cite{Aggarwal2012}. Each of these more complex
@@
 calculates the probability that a given document $d$ belongs to the class $c$.
-The Maximum Entropy approach is summarized below. For a more detailed
-description, see: Nigam et al. \cite{Nigam1999}.
+The Maximum Entropy approach is summarized below (for a more detailed
+description, see: Nigam et al. \cite{Nigam1999}).
 
@@
 
-            \item \textbf{Numbers} are replaced with "\#NUM"
+            \item \textbf{Numbers} are replaced with ``\#NUM''
 
-            \item \textbf{User} are replaced with "@USER"
+            \item \textbf{User} are replaced with ``@USER''
 
-            \item \textbf{Hashtags} are replaced with "\#OCTOTHORPE"
+            \item \textbf{Hashtags} are replaced with ``\#OCTOTHORPE''
 
-            \item \textbf{URLs} are replaced with "@URL"
+            \item \textbf{URLs} are replaced with ``@URL''
 
@@
                 based on their intended meaning. Each group is then replaced
-                with a representation. (e.g. `:)' $\rightarrow$ `EM\_HAPPY' and
-                `;-p' $\rightarrow$ `EM\_WINK')
+                with a representation. [e.g. `:)' $\rightarrow$ `EM\_HAPPY' and
+                `;-p' $\rightarrow$ `EM\_WINK']
 
-            \item most \textbf{Punctuation} is replaced with "PUNCT" however
+            \item most \textbf{Punctuation} is replaced with ``PUNCT'' however
                 question marks, punctuation marks, and ellipsis are each
@@
                 limited size of the dataset only 28 stopwords are used. For a
-                full list of stopwords see section \ref{ssection:stopwords}
+                full list of stopwords see section \ref{ssection:stopwords}.
 
@@
 The implementation created for this project used a \textit{validation set} during
-training as the primary mechanism to avoid overfitting. While training the
-effectiveness of the classifier was evaluated after every iteration, using the
+training as the primary mechanism to avoid overfitting. While training, the
+effectiveness of the classifier was evaluated after every iteration using the
 accuracy or F-positive measure. During the training process the following
@@
             20\% as the \textit{validation set}, and 20\% as the \textit{test set}.
-            Since the Naive Bayes classifier does not use a validation set
-            40\% of the partitions are designated as part of the \textit{test set}
+            Since the Naive Bayes classifier does not use a \textit{validation set},
+            40\% of the partitions are designated as part of the
+            \textit{test set}
 
@@
 classifier without any stopword removal, uncommon word removal (words with a
-document frequancy > 1), Or feature normalization. The F-score that is achieved
-is \textbf{50.72}.
+document frequency $<$ 1), Or feature normalization. The F-score that is
+achieved is \textbf{50.72}.
 
@@
 
-\subsubsection{Number of features}
+\subsubsection{Number of Features}
 \label{ssection:numfeatures}
 
-Number of features retained after feature selection varies from Tweet to Tweet.
-To summarize the number of features retained after different process Table
+The number of features retained after feature selection varies from Tweet to Tweet.
+To summarize the number of features retained after different processes, Table
 \ref{table:numfeatures} presents the mean number of features per Tweet for
@@
 
-As presented in Table \ref{table:numfeatures}, the number of features decreases
-each time a feature set simplification method is turned on. Normalization does
-not appear to significantly reduce the number of features per Tweet. This make
-sense because the number of features in would only be reduced if it contained
-tokens that were different before simplification and were the same after (e.g.
+Interestingly `negative' Tweets contain more features then `positive' Tweets
+which, in turn, contain more features than `neutral' tweets. Normalization does
+not appear to significantly reduce the number of features per Tweet. This makes
+sense since the number of features in the \textit{bag-of-words} would only be
+reduced if two or more of the features are normalized to the same thing (e.g.
 A Tweet that contained `2' and `3' before normalization would only contain the
 feature `\#NUM' after normalization).
-
-%TODO clarify
 
@@
 
-As Table \ref{table:maxent-results} shows `All' experiment provides the best
-results over the baseline. The `Just Stopwords' experiment actually provides
-slightly worse results then the baseline indicating that in context of Tweets
-with so few features in each example every feature counts. The `Just Uncommon'
-experiment does not provide very significant gains when used alone. This is
-potentially due to the fact that with out normalization turned, features such
-as `just' are `Just' are determined to be different and may be removed if each
-only occur once.
+As Table \ref{table:maxent-results} shows, the `All' experiment provides the
+best results over the baseline. The `Just Stopwords' experiment actually
+provides slightly worse results then the baseline indicating that in context of
+Tweets with so few features in each example every feature counts. The `Just
+Uncommon' experiment does not provide very significant gains when used alone.
+This is potentially due to the fact that without normalization turned,
+features such as `just' are `Just' are determined to be different and may be
+removed if each only occur once.
 
@@
 \end{figure}
+
+% TODO make serif?
 
@@
 
-The implementation create for this project has the ability to show which
+The implementation created for this project has the ability to show which
 features are the most discriminatory. The following is a list of the top 30
-most informative features from one run of the Maximum Entropy classifier:
+most informative features from one run of the Maximum Entropy classifier (note
+that some of the weights are negative):
 
@@
 Some of the features listed above make perfect sense, such as `excited' not
-being associated with the neutral class and `shitty' being associated with the
-negative class. However some of the most discriminating features appear in the
-dataset just enough to get past the uncommon word cutoff, such as `calvin' and
-`oneil'.
+being associated with the neutral class and `embarrassing' being associated
+with the negative class. However some of the most discriminating features
+appear in the dataset infrequently, such as `calvin' and `oneil'.
 
@@
 for this project compared to results of the workshop participants. The full
-table (with out this project's results) can be found in table 9 of Nakov et al.
+table (with out this project's results) can be found in Nakov et al. as Table 9
 \cite{Nakov2013}.
@@
 
-As shown in Table \ref{table:comparison} there is a lot of room for improvement
+As shown in Table \ref{table:comparison}, there is a lot of room for improvement
 before this system is a completive solution. However, only simple methods have
@@
 \label{ssection:futurework}
+
+There is room for a number of improvement in the implementation of the system.
+The following sections are a number of improvements as future work. Many of the
+ideas are from the other submissions to the SemEval-2013 workshop.
 
@@
 
-While a simple approach could be to strip the octothorpe from the front of the
-Hashtag (e.g. `\#good' $\rightarrow$ `good'), the semantic meaning of the two
-are different. Hashtags often have message level meaning while simple words
-have local context withing the sentence. Since the dataset created for the
-SemEval-2013 workshop mostly contained examples of Hashtags used as proper
-nouns, more annotated Tweets would be needed for training and testing.
+The words in the previous Tweet carry no inherent sentiment, however the
+message is clearly negative. While a simple approach could be to strip the
+octothorpe from the front of the Hashtag (e.g. `\#good' $\rightarrow$ `good'),
+the semantic meaning of the two are different. Hashtags often have message
+level meaning while simple words have local context withing the sentence. Since
+the dataset created for the SemEval-2013 workshop mostly contained examples of
+Hashtags used as proper nouns, more annotated Tweets would be needed for
+training and testing.
 
-As well Hashtags sometimes use CamelCase to create multi-word tags (e.g.
+Hashtags sometimes use CamelCase to create multi-word tags (e.g.
 `\#SorryNotSorry'). It could prove worthwhile to attempt the decompose
@@
 The top solution from the National Research Council of Canada made use of a
-Hashtag lexicon that they developed between April of 2012 and December of the
-same year \cite{Mohammad2013}. The final \textit{NRC Hashtag Sentiment Lexicon}
-has more than 350,00 entries and is available at
-\href{http://www.saifmohammad.com/WebDocs/NRC-Hashtag-Sentiment-Lexicon-v0.1.zip}{Saif
-Mohammad's website}.
+Hashtag lexicon that they developed between April of 2012 and December 2012
+\cite{Mohammad2013}. The final \textit{NRC Hashtag Sentiment Lexicon} has more
+than 350,00 entries and is available at Saif Mohammad's website
+\footnote{http://www.saifmohammad.com/WebDocs/NRC-Hashtag-Sentiment-Lexicon-v0.1.zip}.
 
@@
 change over time. As well as public perception of a individual changes, the
-prevailing sentiment my change as well.
+prevailing sentiment may change as well.
 
@@
 sequence ``not perfect'' since `not' is a vaguely negative word and `perfect'
-is a very positive word, it would likely be classified as positive when in fact
+is a very positive word. It would likely be classified as positive when in fact
 the sentiment is quite clearly negative. A common approach to this problem is
@@
 
-One way that many of the other bag-of-words solutions capture word order is by
+One way that many of the other \textit{bag-of-words} solutions capture word order is by
 creating features consisting of sequences of words called bigrams. Adding
@@
 uses of sentiment lexicons that capture a term's polarity. These lexicons, such
-as \href{http://sentiwordnet.isti.cnr.it/}{SentiWordNet}, express the positive,
-neutral, and negative sentiment of each homonym.
+as SentiWordNet \footnote{http://sentiwordnet.isti.cnr.it/}, express the
+positive, neutral, and negative sentiment of each homonym. An example of this
+from SentiWordNet, is `good' meaning `morally admirable' having an entirely
+positive sentiment versus `good' meaning `having the normally expected amount'
+having an entirely neutral sentiment
+\footnote{http://sentiwordnet.isti.cnr.it/search.php?q=good}.
 
@@
 
-Many of the top solutions submitted to the workshop such as NRC-Canada
-\cite{Mohammad2013} made use of a support vector machine for classification.
-This indicates that when used effectively a SVM solution can out-perform a
-Maximum Entropy solution. The KLUE team on the other hand found that their
-Maximum Entropy solution outperform their linear SVM solution
-\cite{Proisl2013}.
+Many of the top solutions submitted to the workshop, such as NRC-Canada made
+use of a Support Vector Machine for classification \cite{Mohammad2013}.  This
+indicates that when used effectively a SVM solution can out-perform a Maximum
+Entropy solution. The KLUE team, on the other hand, found that their Maximum
+Entropy solution outperform their linear SVM solution \cite{Proisl2013}.
 
@@
 
-The list of stopwords was acquired \href{www.ranks.nl/stopwords}{here} and is
+The list of stopwords was acquired online\footnote{www.ranks.nl/stopwords} and is
 as follows:
 
-a, about, an, are, as, at, be, by, com, for, from, how, in, is, it, of, on, or,
-that, the, this, to, was, what, when, where, who, will, with
+\begin{Verbatim}[fontsize=\footnotesize]
+        a
+        about
+        an
+        are
+        as
+        at
+        be
+        by
+        com
+        for
+        from
+        how
+        in
+        is
+        it
+        of
+        on
+        or
+        that
+        the
+        this
+        to
+        was
+        what
+        when
+        where
+        who
+        will
+        with
+\end{Verbatim}
 

### 2014-08-05 paper/paper.tex
Changed the instructions to reflect the change in repository name
Fixed the docs to reflex the new brach

@@
 \begin{enumerate}
+
     \item \textbf{Download Source} - The source code is hosted on github.com
-        and can be viewed
-        \href{https://github.com/hockeybuggy/semantic\_eval}{here}. To download a zip
-        file and open it:
+        and can be viewed there
+        \footnote{https://github.com/hockeybuggy/twitter-sentiment}. To download a
+        zip file and open it:
 
 \begin{Verbatim}[fontsize=\footnotesize]
-wget https://github.com/hockeybuggy/semantic_eval/archive/master.zip
-unzip master.zip
-cd master
+wget https://github.com/hockeybuggy/twitter-sentiment/archive/dist.zip -O tsent.zip
+unzip tsent.zip
+cd tsent
 \end{Verbatim}

### 2014-08-07 paper/paper.tex
Made a change to the links in the two readmes
Made the reccomended changes. Still a few more to go

@@
 
-August 4th, 2014 %TODO fix this
+August 7th, 2014 %TODO fix this
 
@@
 
-Draft 4 %TODO ditch this
+Draft 5 %TODO ditch this
 
@@
 
-% TODO expand on IIS
-
 \subsection{Preprocessing and Feature Selection}
@@
 The \textit{Precision} measure for the positive label is $P_{pos} =
-\frac{\mathrm{\# of\ true\ postive}}{\mathrm{\# of\ true\ postive} + \mathrm{\#
-of\ false\ postive} }$. The \textit{Recall} measure for the positive label is
-defined as $R_{pos} = \frac{\mathrm{\# of\ true\ postive}}{\mathrm{\# of\ true\
-postive} + \mathrm{\# of\ false\ negative} }$. $P_{neg}$ and $R_{neg}$ can be
+\frac{\mathrm{\# of\ true\ positive}}{\mathrm{\# of\ true\ positive} + \mathrm{\#
+of\ false\ positive} }$. The \textit{Recall} measure for the positive label is
+defined as $R_{pos} = \frac{\mathrm{\# of\ true\ positive}}{\mathrm{\# of\ true\
+positive} + \mathrm{\# of\ false\ negative} }$. $P_{neg}$ and $R_{neg}$ can be
 calculated in a similar fashion.
+
+Accuracy is used as a secondary performance measure. While more intuitive, it
+is not used as a primary evaluation measure due to it's tendency to be biased
+by uneven numbers of examples particular labels in the dataset. Accuracy,
+henceforth referred to as $Acc$, can be calculate with the following formula:
+
+\begin{equation}
+    Acc = \frac{\mathrm{\# of\ true\ positive} + \mathrm{\# of\ true\ negative}}{N}
+\end{equation}
+
+Where $N$ is equal to the total number of documents in the \textit{test set}.
 
@@
             \textit{test set}
-
-            %TODO is this clear?
 
@@
 
+%TODO change the label names
+
 The following experiments examine the results of the Maximum Entropy classifier
@@
     \begin{center}
-    \begin{tabular}{|c||r|r|r|r|}
+    \begin{tabular}{|r||c|c|c|c|}
         \hline
@@
         \hline
-        All                & 14.85    & 14.06   & 15.10    & 14.49 \\
+        Baseline           & 20.65    & 20.45   & 20.96    & 20.58 \\
         Just Stopwords     & 17.13    & 16.86   & 17.41    & 17.04 \\
@@
         Just Normalization & 19.65    & 19.16   & 20.06    & 19.46 \\
-        Baseline           & 20.65    & 20.45   & 20.96    & 20.58 \\
+        All                & 14.85    & 14.06   & 15.10    & 14.49 \\
         \hline
@@
 \end{table}
-
-%TODO check these results
 
@@
 
+%TODO finish accuracy
+
 \begin{table}[H]
     \begin{center}
-    \begin{tabular}{|r||c|c|c|}
+    \begin{tabular}{|r||c|c|c|c|c|}
         \hline
-        Description    & $\mu F$ & $\sigma F$ & $\delta\ \mu F$ \\
+        Description    & $\mu F$ & $\sigma F$ & $\delta\ \mu F$ & $\mu Acc$ & $\sigma Acc$ \\
         \hline
-        All            & \textbf{50.96} & 1.93 &  2.59 \\
-        Just Stopwords & 48.27   & 1.83 & -0.10 \\
-        Just Uncommon  & 49.02   & 1.96 &  0.65 \\
-        Just Normalize & 49.55   & 2.10 &  1.18 \\
-        Baseline       & 48.37   & 2.15 & - \\
+        Baseline       & 48.37   & 2.15 & -     & & \\
+        Just Stopwords & 48.27   & 1.83 & -0.10 & 62.07 & 1.69 \\
+        Just Uncommon  & 49.02   & 1.96 &  0.65 & 62.47 & 1.91 \\
+        Just Normalize & 49.55   & 2.10 &  1.18 & 63.57 & 1.75 \\
+        All            & \textbf{50.96} & 1.93 &  2.59 & \textbf{63.82} & 0.91 \\
         \hline
@@
 
+%TODO finish table
+
 \begin{table}[H]
     \begin{center}
-    \begin{tabular}{|r||c|c|c|}
+    \begin{tabular}{|r||c|c|c|c|c|}
         \hline
-        Description    & $\mu F$ & $\sigma F$ & $\delta\ \mu F$ \\
+        Description    & $\mu F$ & $\sigma F$ & $\delta\ \mu F$ & $\mu Acc$ & $\sigma Acc$ \\
         \hline
-        All            & 49.28  & 0.81 &  1.17 \\
-        Just Stopwords & 47.29  & 0.76 & -0.82 \\
-        Just Uncommon  & 48.34  & 1.11 &  0.23 \\
-        Just Normalize & \textbf{49.44} & 1.00 & 1.33\\
-        Baseline       & 48.11  & 0.74 & - \\
+        Baseline       & 48.11  & 0.74 & - & & \\
+        Just Stopwords & 47.29  & 0.76 & -0.82 & & \\
+        Just Uncommon  & 48.34  & 1.11 &  0.23 & & \\
+        Just Normalize & \textbf{49.44} & 1.00 & 1.33 & & \\
+        All            & 49.28  & 0.81 &  1.17 & & \\
         \hline
@@
 \end{figure}
-
-% TODO Student T-test
 
@@
         and can be viewed there
-        \footnote{https://github.com/hockeybuggy/twitter-sentiment}. To download a
-        zip file and open it:
+        \footnote{https://github.com/hockeybuggy/twitter-sentiment/tree/dist}.
+        To download a zip file and open it:
 
@@
 \end{Verbatim}
-
-% TODO test this and make a dist branch
 

### 2014-08-07 paper/figures/boxplot.R

@@ -3,7 +3,7 @@ library(ggplot2)
 
 xlab <- "Experiment"
 ylab <- "F-score"
-groups <- c("All", "Just Stopwords", "Just Uncommon", "Just Normalization", "Baseline")
+groups <- c("Baseline", "Just Stopwords", "Just Uncommon", "Just Normalization", "All")
 palette <- c("#999999", "#84B237", "#6E98FF", "#B24932", "#F0E442")
 
 

### 2014-08-08 paper/paper.tex
Fixed the table labels. Changed the download instructions

@@
 Professor Xining Li
-
-\vspace{1.5cm}
-
-Draft 5 %TODO ditch this
 
@@
 
-%TODO change the label names
-
 The following experiments examine the results of the Maximum Entropy classifier
 and the Naive Bayes classifier with various feature selection methods turned on
-or off. The `Baseline' experiment refers to no feature selection. The `Just
-Stopwords' experiment refers the only removing stopwords. The `Just Uncommon'
-experiment refers to only removing words with a document frequency of one. The
-`Just Normalization' experiment refers to only applying feature normalization
-mechanisms. The `All' experiment refers to testing the classifier with all of
-the previous feature selection methods turned on.
+or off. The `Baseline' experiment refers to no feature selection. The `Only
+Stopword Removal' experiment refers the only removing stopwords as feature
+selection. The `Only Rare Word Removal' experiment refers to only removing
+words with a document frequency of 1. The `Only Normalization' experiment
+refers to only applying feature normalization mechanisms. The `All Feature
+Selection' experiment refers to testing the classifier with all of the previous
+feature selection methods turned on.
 
@@
         Baseline               & 20.65    & 20.45   & 20.96    & 20.58 \\
-        Just Stopwords     & 17.13    & 16.86   & 17.41    & 17.04 \\
-        Just Uncommon      & 18.43    & 17.87   & 18.85    & 18.21 \\
-        Just Normalization & 19.65    & 19.16   & 20.06    & 19.46 \\
-        All                & 14.85    & 14.06   & 15.10    & 14.49 \\
+        Only Stopword Removal  & 17.13    & 16.86   & 17.41    & 17.04 \\
+        Only Rare Word Removal & 18.43    & 17.87   & 18.85    & 18.21 \\
+        Only Normalization     & 19.65    & 19.16   & 20.06    & 19.46 \\
+        All Feature Selections & 14.85    & 14.06   & 15.10    & 14.49 \\
         \hline
@@
 
-%TODO finish accuracy
-
 \begin{table}[H]
@@
         \hline
-        Baseline       & 48.37   & 2.15 & -     & & \\
-        Just Stopwords & 48.27   & 1.83 & -0.10 & 62.07 & 1.69 \\
-        Just Uncommon  & 49.02   & 1.96 &  0.65 & 62.47 & 1.91 \\
-        Just Normalize & 49.55   & 2.10 &  1.18 & 63.57 & 1.75 \\
-        All            & \textbf{50.96} & 1.93 &  2.59 & \textbf{63.82} & 0.91 \\
+        Baseline               & 48.37   & 2.15 &     - & \textbf{63.89} & 1.13 \\
+        Only Stopword Removal  & 48.27   & 1.83 & -0.10 & 62.07 & 1.69 \\
+        Only Rare Word Removal & 49.02   & 1.96 &  0.65 & 62.47 & 1.91 \\
+        Only Normalization     & 49.55   & 2.10 &  1.18 & 63.57 & 1.75 \\
+        All Feature Selections & \textbf{50.96}  & 1.93  &  2.59 & 63.82 & 0.91 \\
         \hline
@@
 
-As Table \ref{table:maxent-results} shows, the `All' experiment provides the
-best results over the baseline. The `Just Stopwords' experiment actually
-provides slightly worse results then the baseline indicating that in context of
-Tweets with so few features in each example every feature counts. The `Just
-Uncommon' experiment does not provide very significant gains when used alone.
-This is potentially due to the fact that without normalization turned,
-features such as `just' are `Just' are determined to be different and may be
-removed if each only occur once.
+As Table \ref{table:maxent-results} shows, the `All Feature Selections'
+experiment provides the best results over the baseline. The `Only Stopword
+Removal' experiment actually provides slightly worse results then the baseline
+indicating that in context of Tweets with so few features in each example every
+feature counts. The `Only Rare Words Removal ' experiment does not provide very
+significant gains when used alone.  This is potentially due to the fact that
+without normalization turned, features such as `just' are `Just' are determined
+to be different and may be removed if each only occur once.
 
@@
 
-% TODO make serif?
-
 \subsubsection{Naive Bayes Classifier}
-
-%TODO finish table
 
@@
         \hline
-        Baseline       & 48.11  & 0.74 & - & & \\
-        Just Stopwords & 47.29  & 0.76 & -0.82 & & \\
-        Just Uncommon  & 48.34  & 1.11 &  0.23 & & \\
-        Just Normalize & \textbf{49.44} & 1.00 & 1.33 & & \\
-        All            & 49.28  & 0.81 &  1.17 & & \\
+        Baseline               & 48.11  & 0.74 & -     & 53.13 & 1.48 \\
+        Only Stopword Removal  & 47.29  & 0.76 & -0.82 & 52.71 & 1.16 \\
+        Only Rare Word Removal & 48.34  & 1.11 &  0.23 & 53.92 & 1.32 \\
+        Only Normalization     & \textbf{49.44} & 1.00 & 1.33 & \textbf{55.92} & 0.99 \\
+        All Feature Selections & 49.28  & 0.81 &  1.17 & 54.91 & 1.05 \\
         \hline
@@
 \end{figure}
+
+As Table \ref{table:bayes-results} and Figure \ref{figure:bayes} indicates both
+removing stopwords and removing rare words appear to negatively affect
+performance of the naive bayes classifier.
 
@@
     \begin{center}
+        \small
     \begin{tabular}{|r|l|}
@@
         teragram        & 64.86 \\
-        BOUNCE     & 63.53 \\
-        KLUE       & 63.06 \\
+        BOUNCE*         & 63.53 \\
+        KLUE*           & 63.06 \\
         AMI\&ERIC       & 62.55 \\
@@
         AVAYA           & 60.84 \\
-        SAIL       & 60.14 \\
+        SAIL*           & 60.14 \\
         UT-DB           & 59.87 \\
@@
         UoM             & 51.81 \\
-        \textbf{MaxEnt}& \textbf{50.96} \\
+        \textbf{MaxEnt} & \textbf{50.96} \\
         SSA-UO          & 50.17 \\
         SenselyticTeam  & 50.10 \\
-        $\ldots$   & $\ldots$ \\
-        9 more teams &  \textless\ 50 \\
+        \textbf{Naive Bayes} & \textbf{49.44} \\
+        \textit{9 more teams}&  \textless\ 49 \\
         \hline
@@
     \end{center}
-    \caption{Comparison of constrained classifiers sumitted to the SemEval-2013
-        workshop. Sorted by F-score.}
+    \caption{Comparison of constrained classifiers submitted to the SemEval-2013
+        workshop. Sorted by F-score. * denotes other Maximum Entropy classifiers}
     \label{table:comparison}
 \end{table}
-%TODO add naive bayes
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-wget https://github.com/hockeybuggy/twitter-sentiment/archive/dist.zip -O tsent.zip
-unzip tsent.zip
-cd tsent
+wget https://github.com/hockeybuggy/twitter-sentiment/archive/dist.zip
+unzip dist.zip
+cd twitter-sentiment-dist
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-        a
-        about
-        an
-        are
-        as
-        at
-        be
-        by
-        com
-        for
-        from
-        how
-        in
-        is
+         a                   of
+         about               on
+         an                  or
+         are                 that
+         as                  the
+         at                  this
+         be                  to
+         by                  was
+         com                 what
+         for                 when
+         from                where
+         how                 who
+         in                  will
+         is                  with
          it
-        of
-        on
-        or
-        that
-        the
-        this
-        to
-        was
-        what
-        when
-        where
-        who
-        will
-        with
 \end{Verbatim}

### 2014-08-08 paper/figures/boxplot.R

@@ -3,7 +3,7 @@ library(ggplot2)
 
 xlab <- "Experiment"
 ylab <- "F-score"
-groups <- c("Baseline", "Just Stopwords", "Just Uncommon", "Just Normalization", "All")
+groups <- c("Baseline", "Only Stopword Removal", "Onle Rare Word Removal", "Only Normalization", "All Feature Selections")
 palette <- c("#999999", "#84B237", "#6E98FF", "#B24932", "#F0E442")
 
 

### 2014-08-08 paper/figures/boxplot.R
Fixed the labels on the boxplot

@@ -3,7 +3,7 @@ library(ggplot2)
 
 xlab <- "Experiment"
 ylab <- "F-score"
-groups <- c("Baseline", "Only Stopword Removal", "Onle Rare Word Removal", "Only Normalization", "All Feature Selections")
+groups <- c("Baseline", "Only Stopword Removal", "Only Rare Word Removal", "Only Normalization", "All Feature Selections")
 palette <- c("#999999", "#84B237", "#6E98FF", "#B24932", "#F0E442")
 
 
@@ -18,6 +18,7 @@ p = p + scale_y_continuous(ylab, limits=c(0.35, 0.55))
 p = p + ggtitle(chart_title)
 p = p + scale_fill_manual(values=palette, guide=FALSE)
 p = p + theme_minimal()
+p = p + theme(axis.text.x = element_text(angle=15))
 
 p # Draw that sucker
 ggsave("maxent_boxplot.png")
@@ -34,6 +35,7 @@ p = p + scale_y_continuous(ylab, limits=c(0.35, 0.55))
 p = p + ggtitle(chart_title)
 p = p + scale_fill_manual(values=palette, guide=FALSE)
 p = p + theme_minimal()
+p = p + theme(axis.text.x = element_text(angle=15))
 
 p # Draw that sucker
 ggsave("bayes_boxplot.png")

### 2014-08-08 paper/paper.tex
Made a few small edits in the paper

@@
 labels to select features. While document frequency is the only method employed
-for this project, many other methods exist, such as Gini Index, Information Gain,
-and $\chi^{2}$-statistic \cite{Aggarwal2012}. Each of these more complex
-methods rely on the class label in the training set in order to determine how
-well the feature discriminates between classes.
+for this project, many other methods exist, such as Gini Index, Information
+Gain, and $\chi^{2}$-statistic \cite{Aggarwal2012}. Each of these more complex
+methods rely on the class label in the \textit{training set} in order to
+determine how well the feature discriminates between classes.
 
@@
 
-Accuracy is used as a secondary performance measure. While more intuitive, it
-is not used as a primary evaluation measure due to it's tendency to be biased
-by uneven numbers of examples particular labels in the dataset. Accuracy,
-henceforth referred to as $Acc$, can be calculate with the following formula:
+Accuracy is used as a secondary performance measure. Accuracy, henceforth
+referred to as $Acc$, can be calculate with the following formula:
 
@@
 Where $N$ is equal to the total number of documents in the \textit{test set}.
+While more intuitive, it is not used as the primary evaluation measure due to
+it's tendency to be biased by uneven numbers of examples of particular labels
+in the dataset.
 
@@
 The baseline for this project is established by running the Maximum Entropy
-classifier without any stopword removal, uncommon word removal (words with a
+classifier without any stopword removal, rare word removal (words with a
 document frequency $<$ 1), Or feature normalization. The F-score that is
